### 2023-10-08 latex/paper.tex
Started paper

\documentclass{article}

\title{Inverted Index}

\newcommand{\authorblock}[1]{\begin{tabular}{@{}c@{}}#1\end{tabular}}

\author{\centering\begin{tabular}{ccc}
	\authorblock{
		Aurora Zuoris\\
		\normalsize{aurora.zuoris101@alu.ulgpc.es}
	} &
	\authorblock{
	Alejandra Ruiz de Adana Fleitas\\
	\normalsize{alejandra.ruiz104@alu.ulpgc.es}
	} \\ \\
	\authorblock{
	Lam Truong Nguyen\\
	\normalsize{lam.nguyen101@alu.ulpgc.es}
	} &
	\authorblock{
	Aris Vazdekis Soria\\
	\normalsize{aris.vazdekis101@alu.ulpgc.es}
	} \\ \\
	\authorblock{
	Jaime Ballesteros Domínguez\\
	\normalsize{jaime.ballesteros101@alu.ulpgc.es}
	} &
	\authorblock{
	Anna Barbara Król\\
	\normalsize{anna.krol101@alu.ulpgc.es}
	}
\end{tabular}}

\begin{document}
\maketitle
\abstract{
In this project, we undertook the task of creating an inverted index in Python to enhance search efficiency among a wide variety of text documents.
The primary challenge we faced was the need to quickly access documents containing specific terms within an extensive library.
To accomplish this task, we followed these steps: we collected a hundred English books, tokenized them to split them into words,
built an inverted index that could relate these terms to the specific ID of each book, and developed a series of tables that allowed
us to associate both the tokenized words with the IDs and these IDs with the metadata specific to each book.
}
\end{document}

### 2023-10-08 latex/paper.tex
Finished paper

@@
 \documentclass{article}
+
+\usepackage{minted}
+\usepackage{hyperref}
 
@@
 \abstract{
-In this project, we undertook the task of creating an inverted index in Python to enhance search efficiency among a wide variety of text documents.
+In this project, we undertook the task of creating an inverted index in Python
+to enhance search efficiency among a wide variety of text documents.
 The primary challenge we faced was the need to quickly access documents containing specific terms within an extensive library.
-To accomplish this task, we followed these steps: we collected a hundred English books, tokenized them to split them into words,
-built an inverted index that could relate these terms to the specific ID of each book, and developed a series of tables that allowed
-us to associate both the tokenized words with the IDs and these IDs with the metadata specific to each book.
+To accomplish this task, we followed these steps:
+we collected a hundred English books, tokenized them to split them into words,
+built an inverted index that could relate these terms to the specific ID of each book,
+and developed a series of tables that allowed us to associate both the tokenized words with the IDs and these IDs with the metadata specific to each book.
+As requested, we created several versions of indexers to determine which one was better.
+After conducting the respective tests, we concluded that the NLTK indexer is the most optimal.
 }
+
+\section{Introduction}
+
+In today's world there is an ever increasing
+number of documents that are being created and stored digitally.
+Thus the need to easily find and access these documents becomes
+ever more important. This is where the inverted index comes in.
+An inverted index is a method of creating indices for a given set of documents
+that allows for fast searching of the documents based on the words they contain.
+This is done by creating a dictionary that maps words to sets of documents that contain them.
+
+\section{Methodology}
+
+First, we have made a data collection program that downloads hundreds of documents
+from the Gutenberg Project's collection of documents.
+Then, we have made a data processing program that tokenizes the documents to split them into words and
+create the inverted index.
+For this task, we first gather the data and process
+the relevant documents by loading them from the specified
+directory.
+Next, we will create a reverse keyword index of words
+and documents to enable efficient searching of terms within the documents.
+Finally, we store the results of the indexing in an SQLite database
+for easy access and future querying.
+
+\subsection{Data collection}
+
+For an inverted index to be useful, there must first be a large set of documents to index.
+For this task, we will be using the Gutenberg Project's collection of documents.
+
+First, we are going to import the libraries
+sys, os, json, re, asyncio, and aiohttp.
+Next, we'll create the directory and specify the path where
+we want it to be created. Now, we're going to create 5 functions:
+one for web scraping (transform),
+another to fetch the content of a book in text format,
+one to download the content of a book (fetch),
+one that creates a dictionary with information extracted
+from the text (save\_text),
+and a function that handles the process of downloading
+and storing books (main).
+
+The functions mentioned work as follows:
+
+\begin{itemize}
+	\item In the "transform" function, we will create a list of tuples where each tuple contains the name we will assign to an attribute and a regular expression associated with that attribute to extract the corresponding information from the text.On the other hand, we will also create two regular expressions that will help us find the start and end of the book's content.
+Next, we will create a loop to search for matches in the text using regular expressions, storing that information in the variable "m." In this way, we will check if the variable "m" exists, which means a match has been found.
+If it is verified, we will extract the matching content and store it in a dictionary "data" under the name of the corresponding attribute; otherwise, it will raise an error message.
+Finally, we will take the variables that indicate the start and end of the book's content to extract only the text content in between.
+If an error occurs during this procedure, it will raise an exception.
+	\item The "fetch" function is an asynchronous function used to make an HTTP GET request to a specific URL.
+We will use two arguments: "session" (an aiohttp session for asynchronous HTTP requests) and "id" (the book's identifier).
+We will use the "id" to construct the URL from which we will retrieve the book's content.
+Using the "session" and "id" arguments, we will initiate an asynchronous HTTP request and wait for the response using await response.text(), waiting for the HTTP request to be available and then getting the response content as text.
+This way, the function also retrieves the HTTP response status using response.status and returns it along with the book's content in text format
+	\item The "save\_text" function is an asynchronous function that uses the "fetch" function to retrieve data and save it to a JSON file.
+First, it retrieves some data using the "fetch" function and the "session" and "id" arguments.
+Next, it checks if the status returned by "fetch" is 200.
+If it's not 200, it means there's an error, and it displays an error message indicating that the data could not be obtained for the provided id.
+If the status is 200 (indicating a successful retrieval), it proceeds to process the data in the "text" variable.
+Specifically, it replaces Windows-style line breaks ("{\textbackslash}r{\textbackslash}n") with Unix-style line breaks.
+Then, it calls a function called "transform" with the "id" and the processed "text" as arguments to extract attributes of the book and the main content.
+The result is stored in the "data" variable.
+		Finally, it opens a JSON file in text writing mode.
+The file name is constructed using the provided "id" as part of the file name, and it is created in the directory specified by the "datalake\_dir" variable.
+The "json.dump" function is used to write the content of the "data" variable to the opened JSON file.
+	\item The "main" function starts by creating an asynchronous HTTP session using aiohttp.ClientSession().
+It then asynchronously calls the "save\_text" function to process data in a specific range of values (0 to 999 in this case).
+This allows HTTP requests to be made concurrently to improve the efficiency and performance of the application.
+This concurrent approach is often used in web scraping or data retrieval tasks to speed up the process of fetching data from multiple sources.
+\end{itemize}
+
+Finally, the program will be executed if \_\_name\_\_ == "\_\_main\_\_":, and this will trigger the execution of the "main" function, running the entire program.
+
+\subsection{Data processing}
+
+Once we have the documents, we will need to process them to make them easier to work with.
+This part is implemented in two different ways, each one using
+a different library to tokenize the documents.
+Aditionally, both share some common code, which is abstracted away. This mostly consists
+of accessing the documents in the datalake and saving the results of the indexing
+in an SQLite database.
+
+\subsubsection{spaCy indexer}
+
+\begin{minted}[tabsize=2]{python}
+def indexer(documents):
+	reverse_index = defaultdict(set)
+	for doc_id, document in documents:
+		texto = document.get("text")
+		texto_sobrante = texto
+
+		while len(texto_sobrante) > 0:
+			if len(texto_sobrante) > 1_000_000:
+				candidato = texto_sobrante[:1_000_000]
+				index = candidato.rfind(" ")
+				texto_seccion = texto_sobrante[:index]
+				texto_sobrante = texto_sobrante[index:]
+			else:
+				texto_seccion, texto_sobrante = texto_sobrante, ""
+
+			nlp = spacy.load("en_core_web_sm")
+			doc = nlp(texto_seccion) # Crea un objeto de spacy tipo nlp
+			lexical_tokens = [t.orth_ for t in doc if not (t.is_punct or t.is_stop)]
+			unique_tokens = set(lexical_tokens)
+
+			for word in unique_tokens:
+				reverse_index[word].add(doc_id)
+	return reverse_index
+\end{minted}
+
+The invert indexer pretends to do the following tasks:
+The processing of JSON documents to extract unique token words,
+create a reverse index which is going to be implemented as a dictionary
+and the creation of a database.
+
+The first part of the indexer is a function called indexer which takes
+the documents extracted with the scrapper in JSON format.
+The indexer purpose is to get the content of each document
+and create a unique\_tokens list containing all the words of each document
+which is relevant and not having to account those who are not relevant as
+for example prepositions, conjunctions, questions words, etc.
+
+To make this possible we implemented a library called spacy
+which is capable of reading all the characters in the documents
+and detect only the relevant words.
+These documents are read and divided into smaller sections of text,
+each containing a maximum of one million characters.
+The purpose of this division is to prevent memory issues as the spacy library
+only reads a maximum of four million characters.
+It ensures that these sections are split at appropriate positions (i.e., spaces)
+to avoid breaking words in the middle.
+The loop continues until all portions of the original text have been processed,
+making it suitable for handling extensive textual data efficiently.
+
+Later we have processed the words and tokenized them in a list,
+those words are going to be placed in the reverse index.
+The reverse index is a dictionary where each word is a key,
+and the associated value is a set of document identifiers in which that word appears.
+
+A function called document\_generator generates document data by iterating
+through a directory route which is introduced by the user and must contain
+the documents generated by the datalake. For that iteration we used the tqdm
+library to indicate the progress of reading the books as the database is too long.
+
+Finally when executing the file itself the program takes the arguments introduced by the user,
+expecting two (datalake directory and datamart path).
+Then it creates a table called inv\_index which contains two columns:
+words and list of books. This is the inverted index table.
+Then it is created another table called documents which contains all the metadata of all the documents.
+
+\subsubsection{NLTK indexer}
+
+\begin{minted}[tabsize=2]{python}
+def indexer(document_list):
+	index = defaultdict(set)
+	for doc_id, document in document_list:
+		text = document["text"]
+		words = set(nltk.word_tokenize(text))
+		for word in words:
+			index[word].add(doc_id)
+	return index
+\end{minted}
+
+The second implementation of the indexer uses the NLTK library.
+This python script creates an inverted word index
+from a collection of documents in JSON format.
+The indexer function is defined to create the inverted word index.
+It takes a generator of documents as input. For each document,
+it tokenizes the text into words using NLTK and builds the inverted index,
+associating words with sets of document identifiers in which those words appear.
+With the NLTK library we did not encounter a problem of one million characters limit.
+The document\_generator function generates documents from a specified
+directory (datalake) containing JSON files.
+For each JSON file in the directory, it creates a document identifier
+based on the file name and reads the JSON content,
+returning it as a tuple of the document identifier and document dictionary.
+The script checks the number of command-line arguments.
+% fix
+It expects exactly one argument, which should be the path to the datalake directory containing JSON documents.
+Creating the Inverted Index:
+The main part of the code creates the inverted index by
+calling the indexer function with documents generated by
+the document\_generator function, based on the specified datalake directory.
+Saving the Index to "index.txt":
+The code creates a text file named "index.txt" and writes the inverted
+index data into it. Each line of the file contains a word
+followed by a list of document identifiers where that word is found.
+Displaying Results in the Terminal:
+The script displays the inverted index in the terminal
+showing each word along with the document identifiers where it appears.
+In summary, this script processes JSON documents from a directory, tokenizes the text into words, and constructs an inverted index.
+This version of indexer can be used to efficiently search for and index words within the text data in our search engine project.
+
+\section{Results and conclusions}
+At the end of the tests, we have been able to see that indexing with the NLTK library is faster
+than with spaCy. Among the possible reasons we have found to understand this result are:
+
+\begin{enumerate}
+	\item Model Complexity: SpaCy utilizes more advanced and complex language models designed for in-depth text analysis, which results in longer loading and processing times due to the depth of its analysis.
+	\item NLTK Optimization: NLTK has been optimized for specific text processing tasks like tokenization and text analysis, making it more efficient in these tasks.
+NLTK is faster in extracting keywords and tokens.
+	\item Customization: SpaCy allows for model customization, which can increase accuracy but also slow down the indexing process when detailed adjustments are made.
+\end{enumerate}
+
+In summary, NLTK is faster in indexing due to its lighter and task-specific text processing focus, whereas spaCy excels in deeper text analysis at the cost of higher resource consumption and time.
+
+The code of this project can be found in the following repository: \url{https://github.com/Aurora2500/inverse-index-big-data}
+
+\section{Future work}
+
+There are various ways in which this project could be improved.
+One very critical one is to make it comply with the Gutenberg
+Project's terms of use when it comes to automated downloads.
+This would be done by using one of the mirrors provided by the project,
+as the main site is only meant to be used by humans.
+The issue with this is that surprisingly they're much less
+standardized than the main site, and it would require a lot of work
+to make the scrapper work with them.
+For example, instead of just using the id of the book to download it,
+one would need to split the id into its digits to get the path,
+and then there's also the issue of the file name
+sometimes having a suffix of \texttt{-0} and other times not.
+So it would be impossible to know which one is correct without
+trying both and seeing which one returns a 200 status code and which one doesn't.
+
+In the future, it would be interesting to implement
+a custom indexer trough the use of, for example, regex
+to see if it is possible to improve the performance of the indexer
+and reduce the number of faux tokens.
+One beginning point of this would be to use a regex pattern like
+
+\begin{center}
+\texttt{
+(?<!{\textbackslash}w(?:{\textbackslash}w|'|-))%
+{\textbackslash}b|{\textbackslash}b(?!(?:{\textbackslash}w|'|-)%
+{\textbackslash}w)
+}
+\end{center}
+
+This regex takes the word boundary (\texttt{\textbackslash}b) as a base, and then
+tries to take into account the fact that words can contain apostrophes and hyphens,
+as these would be considered boundaries.
+This way, this regex would match the boundaries of words, including those
+with apostrophes and hyphens such as \texttt{don't} and \texttt{mother-in-law},
+and then one could loop trough the matches to get the words.
+This would be a good starting point, but there is still a lot of work to be done
+for it to be a robust solution.
+
+One of the biggest issues with this project and trying to deal
+with real world data in general is that it is very messy, and not
+necessarily standardized.
+For example, when looking at the metadata, the
+author field is sometimes reffered to as \texttt{author}, other times as \texttt{creator},
+and sometimes as \texttt{contributor}, and there might
+be other variations of this as well.
+Another example is the delimiters between the metadata
+and the document content, which sometimes uses the word \texttt{START OF THIS PROJECT GUTENBERG EBOOK}
+and other times \texttt{START OF THE PROJECT GUTENBERG EBOOK}.
+These are just two of the many examples of the inconsistencies found in the data.
+This leads to the fact that one can't just be clever to
+make a solution in one go, but instead
+one needs to just look trough all
+the data, create some solutions, find
+the issues with them, and then repeat the process
+until the results are satisfactory.
+
+Aditionally, another issue is that the expectations
+of what might be inside a document aren't always accurate.
+For example, some documents were about listing some
+famous mathematical constants to a very big number of digits,
+so the edge case of a document consisting of mostly
+numbers with no word boundaries, or of these
+being split by newlines and what to do with these
+should also be considered.
+Another example is that some documents consisted
+of dictionaries of words or some other similar
+glossaries, so virtually every word would appear in these documents.
+And there may be many other different kinds of documents
+that contain their own edge cases. Some that we might
+not even be aware of.
+
 \end{document}

### 2023-10-08 indexer/spacy_indexer.py

@@ -9,36 +9,34 @@ from collections import defaultdict
 from indexer_commons import document_generator, create_datamart
 
 def indexer(documents):
-    reverse_index = defaultdict(set)
-    for doc_id, document in documents:
-        texto = document.get("text")
-        texto_sobrante = texto
+	reverse_index = defaultdict(set)
+	for doc_id, document in documents:
+		texto = document.get("text")
+		texto_sobrante = texto
 
-        while len(texto_sobrante) > 0:
-            if len(texto_sobrante) > 1_000_000:
-                candidato = texto_sobrante[:1_000_000]
-                index = candidato.rfind(" ")
-                texto_seccion = texto_sobrante[:index]
-                texto_sobrante = texto_sobrante[index:]
-            else:
-                texto_seccion, texto_sobrante = texto_sobrante, ""
+		while len(texto_sobrante) > 0:
+			if len(texto_sobrante) > 1_000_000:
+				candidato = texto_sobrante[:1_000_000]
+				index = candidato.rfind(" ")
+				texto_seccion = texto_sobrante[:index]
+				texto_sobrante = texto_sobrante[index:]
+			else:
+				texto_seccion, texto_sobrante = texto_sobrante, ""
 
-            nlp = spacy.load("en_core_web_sm")
-            doc = nlp(texto_seccion) # Crea un objeto de spacy tipo nlp
-            lexical_tokens = [t.orth_ for t in doc if not (t.is_punct or t.is_stop)]
+			nlp = spacy.load("en_core_web_sm")
+			doc = nlp(texto_seccion) # Crea un objeto de spacy tipo nlp
+			lexical_tokens = [t.orth_ for t in doc if not (t.is_punct or t.is_stop)]
+			unique_tokens = set(lexical_tokens)
 
-            unique_tokens = set(lexical_tokens)
+			for word in unique_tokens:
+				reverse_index[word].add(doc_id)
+	return reverse_index
 
-                
-            for word in unique_tokens:
-                reverse_index[word].add(doc_id)
-    return reverse_index
-        
 if __name__ == "__main__":
-    if len(sys.argv) < 3:
-        print("Usage: python spacy_index.py <datalake> <datamart>")
-        exit(1)
-    datalake_dir = sys.argv[1]
-    index = indexer(document_generator(datalake_dir))
-    datamart_path = sys.argv[2]
-    create_datamart(datalake_dir, datamart_path, index)
[…]

### 2023-10-09 latex/paper.tex

@@
 the document\_generator function, based on the specified datalake directory.
-Saving the Index to "index.txt":
-The code creates a text file named "index.txt" and writes the inverted
-index data into it. Each line of the file contains a word
-followed by a list of document identifiers where that word is found.
-Displaying Results in the Terminal:
-The script displays the inverted index in the terminal
-showing each word along with the document identifiers where it appears.
+Saving the Index to SQLite database:
+Create datamart function creates two tables in an SQLite database: "inv index" and "documents". 
+The first table stores an inverted index mapping words to document IDs, while the second table stores information about documents, such as their titles, dates, and content.
+The code writes the inverted index data into it.
 In summary, this script processes JSON documents from a directory, tokenizes the text into words, and constructs an inverted index.

### 2023-10-09 indexer/manual_indexer.py
Fixed removal of common

@@ -1,11 +1,0 @@
-import os
-import sys
-import json
-import tqdm
-from collections import defaultdict
-
-def indexer(document_list):
-	index = defaultdict(set)
-	for doc_id, doc in document_list:
-		pass
-	return index

### 2023-10-09 indexer/nltk_indexer.py

@@ -1,72 +1,36 @@
-import os
 import sys
-import json
-import re
 import nltk
-
 from collections import defaultdict
+from indexer_commons import document_generator, create_datamart
 
 def indexer(document_list):
-    """
-    Creates an inverted word index based on a list of documents.
+	"""
+	Creates an inverted word index based on a list of documents.
+	Args:
+		document_list (generator): A generator of tuples (doc_id, document), where
+			doc_id is the document identifier, and document is a dictionary containing
+			a 'text' key with the document's text.
+	Returns:
+		defaultdict: The inverted word index where keys are words, and values are sets
+		of document identifiers containing that word.
+	"""
+	index = defaultdict(set)
+	for doc_id, document in document_list:
+		text = document["text"]
+		# Tokenize the text into words using NLTK
+		words = set(nltk.word_tokenize(text))
+		for word in words:
+			index[word].add(doc_id)
+	return index
 
-    Args:
-        document_list (generator): A generator of tuples (doc_id, document), where
-            doc_id is the document identifier, and document is a dictionary containing
-            a 'text' key with the document's text.
+if __name__ == "__main__":
+	if len(sys.argv) < 3:
+		print("Usage: python nltk_indexer.py <datalake> <datamart>")
+		exit(1)
+	# Ścieżka do katalogu z plikami JSON
+	datalake_path = sys.argv[1]
 
-    Returns:
-        defaultdict: The inverted word index where keys are words, and values are sets
-        of document identifiers containing that word.
-    """
-    index = defaultdict(set)
-    for doc_id, document in document_list:
-        text = document["text"]
-        # Tokenize the text into words using NLTK
-        words = set(nltk.word_tokenize(text))
-        for word in words:
-            index[word].add(doc_id)
-    return index
+	index = indexer(document_generator(datalake_path))
 
-def document_generator(datalake):
-    """
-    Generates documents from a datalake directory containing JSON files.
-
-    Args:
-        datalake (str): The path to the directory containing JSON files.
-
-    Yields:
-        tuple: A tuple containing a document identifier and a document dictionary.
-    """
-    books = os.listdir(datalake)
-    for book in books:
-        # Combine the full path with the filename
-        archivo = os.path.join(datalake, book)
-
-        # Check if the file is a JSON file
-        if book.endswith('.json'):
-            doc_id = int(book[:-5])
-            with open(archivo, 'r', encoding='utf-8') as archivo_json:
[…]

### 2023-10-09 indexer/spacy_indexer.py

@@ -3,89 +3,40 @@ import json
 import os
 import sys
 import spacy  
-import sqlite3
 from tqdm import tqdm
-
 from collections import defaultdict
 
+from indexer_commons import document_generator, create_datamart
+
 def indexer(documents):
-    reverse_index = defaultdict(set)
-    for doc_id, document in documents:
-        texto = document.get("text")
-        texto_sobrante = texto
+	reverse_index = defaultdict(set)
+	for doc_id, document in documents:
+		texto = document.get("text")
+		texto_sobrante = texto
 
-        while len(texto_sobrante) > 0:
-            if len(texto_sobrante) > 1_000_000:
-                candidato = texto_sobrante[:1_000_000]
-                index = candidato.rfind(" ")
-                texto_seccion = texto_sobrante[:index]
-                texto_sobrante = texto_sobrante[index:]
-            else:
-                texto_seccion, texto_sobrante = texto_sobrante, ""
+		while len(texto_sobrante) > 0:
+			if len(texto_sobrante) > 1_000_000:
+				candidato = texto_sobrante[:1_000_000]
+				index = candidato.rfind(" ")
+				texto_seccion = texto_sobrante[:index]
+				texto_sobrante = texto_sobrante[index:]
+			else:
+				texto_seccion, texto_sobrante = texto_sobrante, ""
 
-            nlp = spacy.load("en_core_web_sm")
-            doc = nlp(texto_seccion) # Crea un objeto de spacy tipo nlp
-            lexical_tokens = [t.orth_ for t in doc if not (t.is_punct or t.is_stop)]
+			nlp = spacy.load("en_core_web_sm")
+			doc = nlp(texto_seccion) # Crea un objeto de spacy tipo nlp
+			lexical_tokens = [t.orth_ for t in doc if not (t.is_punct or t.is_stop)]
+			unique_tokens = set(lexical_tokens)
 
-            unique_tokens = set(lexical_tokens)
-
-                
-            for word in unique_tokens:
-                reverse_index[word].add(doc_id)
-    return reverse_index
-        
-def document_generator(ruta):
-    libros = os.listdir(ruta)
-    for libro in tqdm(libros):
-        # Combinamos la ruta completa con el nombre del archivo
-        archivo = os.path.join(ruta, libro)
-
-        # Verificamos si el archivo es un archivo JSON
-        if libro.endswith('.json'):
-            doc_id = int(libro[:-5])
[…]

### 2023-10-09 indexer/indexer_commons.py
Fixed tqdm import

@@ -1,7 +1,7 @@
 import json
 import os
 import sqlite3
-import tqdm
+from tqdm import tqdm
 
 def document_generator(datalake):
 	books = os.listdir(datalake)

### 2023-10-09 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/Main.java
init java impl

@@ -1,0 +1,7 @@
+package es.ulpgc.bigdata.inverse_index;
+
+public class Main {
+	public static void main(String[] args) {
+		System.out.println("Hello world!");
+	}
+}

### 2023-11-04 InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/ContentExtractor.java
crawler

@@ -6,6 +6,7 @@ import java.io.InputStreamReader;
 import java.net.HttpURLConnection;
 import java.net.URL;
 
+
 public class ContentExtractor {
 
     public static String textExtractor(int id) {

### 2023-11-04 InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/Controller.java

@@ -1,0 +1,60 @@
+package es.ulpgc.bigdata;
+
+import java.io.File;
+import java.util.Timer;
+import java.util.TimerTask;
+
+import static spark.Spark.init;
+import static spark.Spark.port;
+
+public class Controller {
+    private TimerTask task;
+    private File datalakeRoot;
+
+    public Controller(File datalakeRoot) {
+        this.datalakeRoot = datalakeRoot;
+    }
+
+    public void start() {
+        Timer timer = new Timer();
+        task = new TimerTask() {
+            public void run() {
+                executeProgram();
+            }
+        };
+        timer.scheduleAtFixedRate(task, 0, TimerAPI.getTimerPeriod());
+    }
+
+    private void executeProgram() {
+        ContentExtractor contentExtractor = new ContentExtractor();
+        FileSystemDatalake dataLake = new FileSystemDatalake(datalakeRoot);
+
+        int id = 1;
+        int millisecondsPerMinute = 60_000;
+
+        while (id <= TimerAPI.getMaxBooks()) {
+            long startTime = System.currentTimeMillis();
+            int booksDownloadedThisMinute = 0;
+
+
+            while (booksDownloadedThisMinute < TimerAPI.getBooksPerMinute()) {
+                String bookText = ContentExtractor.textExtractor(id);
+
+                if (bookText != null) {
+                    FileSystemDatalake.saveText(id, bookText);
+                    booksDownloadedThisMinute++;
+                }
+                id++;
+            }
+
+            long elapsedTime = System.currentTimeMillis() - startTime;
+            if (elapsedTime < millisecondsPerMinute) {
+                try {
+                    Thread.sleep(millisecondsPerMinute - elapsedTime);
+                } catch (InterruptedException e) {
+                    e.printStackTrace();
+                }
+            }
+        }
+    }
+}

### 2023-11-04 InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/LibroGutenberg.java

@@ -1,5 +1,4 @@
 package es.ulpgc.bigdata;
-
 import java.util.*;
 import java.util.regex.Matcher;
 import java.util.regex.Pattern;

### 2023-11-04 InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/Main.java

@@ -3,30 +3,22 @@ package es.ulpgc.bigdata;
 import java.io.File;
 
 
+import java.io.File;
+
+import static java.lang.Thread.sleep;
+import static spark.Spark.init;
+import static spark.Spark.port;
+
 public class Main {
+    public static void main(String[] args) throws InterruptedException {
+        port(4567);
+        TimerAPI.setupTimerAPI();
+        init();
 
-    public static void main(String[] args) {
-        //this is the datalake root file taken in arguments
         File datalakeRoot = new File(args[0]);
-        new ContentExtractor();
-        new FileSystemDatalake(datalakeRoot);
+        Controller controller = new Controller(datalakeRoot);
+        controller.start();
 
-        //below here it must be the timer with the execution rules
-
-        int id = 1; //first book id
-
-        while (id <= 1000) { //how much we want
-            //below here we call the textExtractor function that will make the HTTP request and obtain the text of the book
-            String bookText = ContentExtractor.textExtractor(id);
-
-            //if the text is valid, we save it in the datalake root calling the function saveText
-            if (bookText != null) {
-                FileSystemDatalake.saveText(id, bookText);
-            }
-
-            id++; //increment the id to get the next book in the following iteration
-        }
     }
 }
-
 

### 2023-11-04 InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/TimerAPI.java

@@ -1,0 +1,61 @@
+package es.ulpgc.bigdata;
+
+import static spark.Spark.*;
+
+public class TimerAPI {
+    private static long timerPeriod = 5 * 60_000; // 5 minutes in milliseconds by default
+    private static int booksPerMinute = 100; // 100 books per minute by default
+    private static int maxBooks = 1000; // 1000 max books by default
+
+    public static void setupTimerAPI() {
+        post("/v1/execution/configuration", (request, response) -> {
+            System.out.println("\n");
+            if (request.queryParams().contains("maxbooks")) {
+                int max = Integer.parseInt(request.queryParams("maxbooks"));
+                setMaxBooks(max);
+                System.out.println("Max books successfully setted on: " + getMaxBooks());
+            }
+            if (request.queryParams().contains("booksperminute")) {
+                int books = Integer.parseInt(request.queryParams("booksperminute"));
+                setBooksPerMinute(books);
+                System.out.println("Books per minute successfully settled on: " + getBooksPerMinute());
+
+            }
+            if (request.queryParams().contains("timerperiod")) {
+                long minutes = Long.parseLong(request.queryParams("timerperiod"));
+                setTimerPeriod(minutes);
+                System.out.println("Timer period successfully settled on: " + getTimerPeriod()/60_000 + " minutes");
+
+            }
+            System.out.println("\n");
+            response.status(200);
+            response.body("Execution configuration set successfully. Max books: " + getMaxBooks() + ", Books per minute: " + getBooksPerMinute() + " and Timer period set on: " + getTimerPeriod() / 60_000 + " minutes.");
+            return null;
+        });
+
+    }
+
+    public static void setTimerPeriod(long minutes) {
+        timerPeriod = minutes * 60_000;
+    }
+
+    public static void setBooksPerMinute(int books) {
+        booksPerMinute = books;
+    }
+
+    public static void setMaxBooks(int max) {
+        maxBooks = max;
+    }
+
+    public static long getTimerPeriod() {
+        return timerPeriod;
+    }
+
+    public static int getBooksPerMinute() {
+        return booksPerMinute;
+    }
+
+    public static int getMaxBooks() {
+        return maxBooks;
+    }
+}

### 2023-11-04 InverseIndex/DatamartTest/src/main/java/org/example/MetadataExtractor.java

@@ -10,74 +10,61 @@ import java.util.Objects;
 
 public class MetadataExtractor {
 
-    public void filter() {
-        String datalakeDir = "C:/Users/Jaime/Desktop/Datalake/";
-        File datalake = new File(datalakeDir);
-        File[] folders = datalake.listFiles();
+    public void filter(File datalake) {
+        File[] books = datalake.listFiles();
+
 
         try {
-            if (folders != null) {
+            if (books != null) {
+                for (File book : books) {
+                    String fileName = book.getName();
+                    System.out.println(fileName);
 
-                for (File folder : folders) {
+                    if (fileName.endsWith(".json")) {
+                        int docId = Integer.parseInt(fileName.substring(0, fileName.length() - 5));
+                        ObjectMapper objectMapper = new ObjectMapper();
+                        JsonNode rootNode = objectMapper.readTree(book);
 
-                    String folderName = folder.getName();
-                    String newDatalakeDir = datalakeDir + folderName + "/";
-                    File newDatalake = new File(newDatalakeDir);
-                    File[] books = newDatalake.listFiles();
-                    System.out.println(folderName);
+                        String date = null;
+                        String author = null;
+                        String text = null;
+                        String title = null;
+                        String lang = null;
 
-                    if (books != null) {
-                        for (File book : books) {
-                            String fileName = book.getName();
-                            System.out.println(fileName);
-
-                            if (fileName.endsWith(".json")) {
-                                int docId = Integer.parseInt(fileName.substring(0, fileName.length() - 5));
-                                ObjectMapper objectMapper = new ObjectMapper();
-                                JsonNode rootNode = objectMapper.readTree(new File(newDatalakeDir + fileName));
-
-                                String date = null;
-                                String author = null;
-                                String text = null;
-                                String title = null;
-                                String lang = null;
-
-                                if (rootNode.has("date")) {
-                                    date = rootNode.get("date").asText();
-                                }
-
-                                if (rootNode.has("author")) {
-                                    author = rootNode.get("author").asText();
-                                }
-
-                                if (rootNode.has("text")) {
-                                    text = rootNode.get("text").asText();
-                                }
-
-                                if (rootNode.has("title")) {
-                                    title = rootNode.get("title").asText();
-                                }
-
-                                if (rootNode.has("lang")) {
-                                    lang = rootNode.get("lang").asText();
-                                }
-
-
-                                Book content = new Book(docId, date, author, text, title, lang);
-
[…]

### 2023-11-04 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/Main.java

@@ -1,14 +1,7 @@
 package es.ulpgc.bigdata.inverse_index;
 
-import spark.Spark;
-
 public class Main {
 	public static void main(String[] args) {
-		System.out.println("Hello world!");
-		Spark.port(8080);
-		Spark.get("/", (request, response) -> {
-
-			return "woah";
-		});
+		new Controller().startServers();
 	}
 }

### 2023-11-04 InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/FileDatalake.java
Implemented Indexer

@@ -1,37 +1,0 @@
-package es.ulpgc.bigdata.inverse_index;
-
-import java.io.IOException;
-import java.nio.file.Files;
-import java.nio.file.Path;
-import java.nio.file.WatchService;
-import java.util.HashSet;
-import java.util.Set;
-import java.util.function.Predicate;
-import java.util.regex.Pattern;
-
-public class FileDatalake {
-	private final Path root;
-
-	public FileDatalake(Path root) {
-		this.root = root;
-	}
-
-
-	public Set<Integer> documents() throws IOException {
-		Set<Integer> documents = new HashSet<>();
-		Predicate<String> isDocument = Pattern.compile("\\d+\\.json").asMatchPredicate();
-		for (Path document: Files.list(root).toList()) {
-			if (!Files.isRegularFile(document)) continue;
-			String name = document.getFileName().toString();
-			if (!isDocument.test(name)) continue;
-			documents.add(Integer.parseInt(name.split("\\.")[0]));
-		}
-		return documents;
-	}
-
-	public WatchService watchService() throws IOException {
-		WatchService ws = root.getFileSystem().newWatchService();
-		root.register(ws, java.nio.file.StandardWatchEventKinds.ENTRY_CREATE, java.nio.file.StandardWatchEventKinds.ENTRY_MODIFY);
-		return ws;
-	}
-}

### 2023-11-04 InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/Indexer.java

@@ -1,38 +1,0 @@
-package es.ulpgc.bigdata.inverse_index;
-
-import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
-
-import java.nio.file.WatchService;
-import java.util.Set;
-
-public class Indexer {
-	private final FileDatalake datalake;
-	private final Datamart datamart;
-
-	public Indexer(FileDatalake datalake, Datamart datamart) {
-		this.datalake = datalake;
-		this.datamart = datamart;
-	}
-
-	private Set<String> tokenize(String document) {
-		return null;
-	}
-
-	private Set<String> tokenizeDocument(int document) {
-		return null;
-	}
-
-	public void index() throws Exception {
-		// get already indexed documents
-		Set<Integer> indexedDocuments = datamart.documents();
-		Set<Integer> datalakeDocuments = datalake.documents();
-		datalakeDocuments.removeAll(indexedDocuments);
-		for (Integer document: datalakeDocuments) {
-			Set<String> tokens = tokenizeDocument(document);
-			datamart.add(document, tokens);
-		}
-
-		WatchService watchService = datalake.watchService();
-
-	}
-}

### 2023-11-04 InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/Main.java

@@ -1,16 +1,0 @@
-package es.ulpgc.bigdata.inverse_index;
-
-import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
-import es.ulpgc.bigdata.inverse_index.datamart.file.FileDatamart;
-
-import java.io.IOException;
-import java.nio.file.Path;
-
-public class Main {
-	public static void main(String[] args) throws IOException {
-		FileDatalake datalake = new FileDatalake(Path.of(args[1]));
-		Datamart datamart = new FileDatamart(Path.of(args[2]));
-		Indexer indexer = new Indexer(datalake, datamart);
-		indexer.index();
-	}
-}

### 2023-11-04 InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/IndexerState.java

@@ -1,0 +1,12 @@
+package es.ulpgc.bigdata.inverse_index.indexer;
+
+public enum IndexerState {
+	// it is a regular token, but it is not finished yet, add it to the current token when it is finished
+	InToken,
+	// the current token is valid, but it has some trailing characters that aren't valid if they're the last ones
+	InValidTokenUnknownEnd,
+	// Even though we are in a token, it is not valid and thus we should ignore it and go to the next one
+	InInvalidToken,
+	OutOfToken,
+
+}

### 2023-11-04 InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/Main.java

@@ -1,0 +1,24 @@
+package es.ulpgc.bigdata.inverse_index.indexer;
+
+import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
+import es.ulpgc.bigdata.inverse_index.datamart.file.FileDatamart;
+
+import java.nio.file.Path;
+
+public class Main {
+	public static void main(String[] args) throws Exception {
+		//assert that the arguments are correct
+		if (args.length != 2) {
+			System.out.println("Usage: java -jar indexer.jar <datalake> <datamart>");
+			System.out.println("Num args: " + args.length);
+			for(String arg: args) {
+				System.out.println(arg);
+			}
+			System.exit(1);
+		}
+		FileDatalake datalake = new FileDatalake(Path.of(args[0]));
+		Datamart datamart = new FileDatamart(Path.of(args[1]));
+		Indexer indexer = new Indexer(datalake, datamart);
+		indexer.index();
+	}
+}

### 2023-11-05 latexJava/paperJava.tex
Starting with paper for Java
Update paperJava.tex

--- 2023-10-08 latex/paper.tex
@@
 
-\title{Inverted Index}
+\usepackage{minted}
+\usepackage{hyperref}
+
+\title{Crawler and Inverted Index in Java}
 
@@
 \abstract{ 
-In this project, we undertook the task of creating an inverted index in Python to enhance search efficiency among a wide variety of text documents.
+In this project, we undertook the task of transforming code in Java to enhance search efficiency among a wide variety of text documents.
 The primary challenge we faced was the need to quickly access documents containing specific terms within an extensive library.
-To accomplish this task, we followed these steps: we collected a hundred English books, tokenized them to split them into words,
-built an inverted index that could relate these terms to the specific ID of each book, and developed a series of tables that allowed
-us to associate both the tokenized words with the IDs and these IDs with the metadata specific to each book.
+Our code encompasses three concurrent modules: Crawler, Indexer and QueryEngine, all working in unison to ensure seamless operation.
+To ensure optimal performance, we integrated a timer mechanism that defaults to downloading 100 books per minute.
+%To accomplish this task, we followed these steps:
+%we collected a hundred English books, tokenized them to split them into words, built an inverted index that could relate these terms to the specific ID of each book, and developed a series of tables that allowed us to associate both the tokenized words with the IDs and these IDs with the metadata specific to each book.
+%tu dodac co porownujemy i co lepsze
 }
+
+\section{Introduction}
+In today's world there is an ever increasing
+number of documents that are being created and stored digitally.
+Thus the need to easily find and access these documents becomes
+ever more important. This is where the inverted index comes in.
+An inverted index is a method of creating indices for a given set of documents that allows for fast searching of the documents based on the words they contain.
+The 'crawler' module is responsible for retrieving, processing, and storing textual content from books available on the Gutenberg.org website.
+It systematically downloads and handles book content, ensuring that these texts are integrated seamlessly into the inverted index.
+
+\section{Methodology}
+
+First, we
+
+\subsection{Crawler}
+
+The "Crawler" module consists of a set of interconnected classes, each contributing to the execution of this complex task.
+This detailed description sheds light on how these classes work together in the process of downloading and handling book content.
+The classes mentioned work as follows:
+\begin{itemize}
+\item
+The \texttt{ContentExtractor} class plays a fundamental role in the process by fetching text from specific books hosted on Gutenberg.org.
+It is capable of extracting textual data from the site using HTTP requests.
+To initiate the process, it requires a unique book identifier, and upon successful retrieval, it returns the book's text.
+This class serves as the initial point of contact with the online library.
+\item
+The \texttt{FileSystemDatalake} class is responsible for the storage and management of the downloaded textual content.
+It converts the raw book text into JSON format and stores it in files, with each file named after the respective book's identifier.
+This class plays a crucial role in creating and maintaining the Datalake directory structure, ensuring organized and efficient data storage.
+\item
+The \texttt{LibroGutenberg} class is pivotal in the process of extracting meaningful information from the downloaded book text.
+It utilizes regular expressions to search for and identify various attributes, such as the book's title, author, publication date, language, and, most importantly, the book's actual textual content.
+This class ensures the structured extraction of metadata and book text.
+\item
+The \texttt{TimerAPI} class provides an interface for configuring essential parameters related to the book retrieval process.
+It allows for the adjustment of the execution period, which determines how frequently the system fetches new books.
+Additionally, it enables users to specify the number of books to download per minute and set a maximum limit for the number of books to retrieve.
+This class is accessible through an HTTP interface, making it a valuable tool for process customization.
+\item
+The \texttt{Controller} class serves as the orchestrator of the entire process.
+It initiates a timer that cyclically triggers the execution of operations for downloading and saving book texts.
+During this continuous process, it leverages the functionality of the \texttt{ContentExtractor}, \texttt{FileSystemDatalake}, and \texttt{LibroGutenberg} classes.
+By doing so, it ensures that books are fetched, processed, and stored systematically.
+\end{itemize}
+The complete workflow of the "crawler" module can be summarized as follows:
+
+1. Parameters for the download frequency, books per minute, and the maximum number of books to retrieve are configured using the \texttt{TimerAPI} class.
+
+2.
+The main \texttt{Main} class initializes the entire system.
+It sets the port for the system, initializes the Spark server, and passes the location of the Datalake directory to the \texttt{Controller} class.
+
+3.
+The \texttt{Controller} class takes charge of initiating the process of downloading book texts.
+The process is repetitive and continues until the maximum number of books is reached or other predefined termination criteria are met.
+
+4.
+The \texttt{ContentExtractor} class is employed to retrieve textual content from specific books, while the \texttt{LibroGutenberg} class handles the subsequent processing of the text, extracting valuable attributes.
+
+5.
+The \texttt{FileSystemDatalake} class manages the storage of the downloaded text in JSON format.
+It is responsible for creating a structured directory hierarchy, facilitating efficient data storage.
+
+The "crawler" module serves as a vital component within the system, enabling the retrieval, structured processing, and organized storage of textual content from the Gutenberg.org website.
+This content can subsequently be accessed and utilized in various ways, making it a versatile and valuable module for data acquisition and management.
+
+\subsection{Indexer}
+\subsection{Query Engine}
+
+\section{Results and conclusions}
+
+The code of this project can be found in the following repository: \url{https://github.com/Aurora2500/inverse-index-big-data}
+
+\section{Future work}
+
+There are various ways in which this project could be improved.
+
 \end{document}

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/Controller.java
crawler

@@ -6,6 +6,8 @@ package es.ulpgc.bigdata.inverse_index;
 public class Controller {
     public void startServers() {
         SparkWebService sparkWebService = new SparkWebService();
-        sparkWebService.startServerById();
+        //sparkWebService.startServerById();
+        sparkWebService.startServerByDocument();
+
     }
 }

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/SparkWebService.java

@@ -6,6 +6,8 @@ package es.ulpgc.bigdata.inverse_index;
 import com.google.gson.Gson;
 import spark.Spark;
 
+import java.util.List;
+
 public class SparkWebService {
 
     public void startServerById() {
@@ -39,26 +41,26 @@ public class SparkWebService {
         Spark.port(4567);
 
         Spark.get("/v1/search", (request, response) -> {
-            String id = request.queryParams("word");
+            String word = request.queryParams("word");
 
             try {
-                int documentId = Integer.parseInt(id);
-                Document document = SqliteReader.retrieveDocumentInfo(documentId);
+                SqliteReader sqliteReader = new SqliteReader();  // Crea una instancia de la clase SqliteReader
+                List<String> books = sqliteReader.getBooksForWord(word);
 
-                if (document != null) {
+                if (!books.isEmpty()) {
+                    List<Document> documents = sqliteReader.getMetadataForBooks(books);
                     Gson gson = new Gson();
                     response.type("application/json");
-                    return gson.toJson(document);
+                    return gson.toJson(documents);
                 } else {
                     response.status(404); // Not Found
-                    return "Documento no encontrado para el ID especificado.";
+                    return "Documentos no encontrados para la palabra especificada.";
                 }
-            } catch (NumberFormatException e) {
+            } catch (Exception e) {
                 response.status(400); // Bad Request
-                return "ID no válido. Debe ser un número entero.";
+                return "Error al procesar la solicitud: " + e.getMessage();
             }
         });
     }
 }
-
 

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/SqliteReader.java

@@ -4,6 +4,9 @@ import java.sql.Connection;
 import java.sql.DriverManager;
 import java.sql.PreparedStatement;
 import java.sql.ResultSet;
+import java.util.ArrayList;
+import java.util.Arrays;
+import java.util.List;
 
 
 public class SqliteReader {
@@ -35,47 +38,74 @@ public class SqliteReader {
         return document;
     }
 
-    public static Document retrieveDocumentInfo(int id) {
-        Document document = null;
+    public List<String> getBooksForWord(String word) {
+        List<String> books = new ArrayList<>();
         String url = "jdbc:sqlite:metadata.db";
 
         try (Connection connection = DriverManager.getConnection(url);
-             PreparedStatement preparedStatement = connection.prepareStatement("SELECT id, date, author, text, title, lang FROM metadata WHERE id = ?")) {
-            preparedStatement.setInt(1, id);
+             PreparedStatement preparedStatement = connection.prepareStatement("SELECT word, book FROM words WHERE word = ?")) {
+            preparedStatement.setString(1, word);
             ResultSet resultSet = preparedStatement.executeQuery();
 
             if (resultSet.next()) {
-                int documentId = resultSet.getInt("id");
-                String date = resultSet.getString("date");
-                String author = resultSet.getString("author");
-                String title = resultSet.getString("title");
-                String lang = resultSet.getString("lang");
+                String booksStr = resultSet.getString("book");
+                books = Arrays.asList(booksStr.split(", ")); // Supongamos que los libros están separados por comas
+            }
+        } catch (Exception e) {
+            e.printStackTrace();
+        }
+        return books;
+    }
 
-                String text = resultSet.getString("text");
-                if (text != null) {
-                    // Split the text into words
-                    String[] words = text.split("\\s+");
+    public List<Document> getMetadataForBooks(List<String> books) {
+        ArrayList<Document> documents = new ArrayList<>();
+        String url = "jdbc:sqlite:metadata.db";
 
-                    // Take the first 200 words or less if the text has less than 200 words
-                    StringBuilder first200Words = new StringBuilder();
-                    for (int i = 0; i < Math.min(words.length, 200); i++) {
-                        first200Words.append(words[i]).append(" ");
+        try (Connection connection = DriverManager.getConnection(url)) {
+            for (String book : books) {
+                try (PreparedStatement preparedStatement = connection.prepareStatement("SELECT id, title, text, lang, date, author FROM metadata WHERE title = ?")) {
[…]

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/Controller.java
crawler

@@ -6,8 +6,6 @@ package es.ulpgc.bigdata.inverse_index;
 public class Controller {
     public void startServers() {
         SparkWebService sparkWebService = new SparkWebService();
-        //sparkWebService.startServerById();
-        sparkWebService.startServerByDocument();
-
+        sparkWebService.startServer();
     }
 }

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/SparkWebService.java

@@ -10,57 +10,56 @@ import java.util.List;
 
 public class SparkWebService {
 
-    public void startServerById() {
+    public void startServer() {
         Spark.port(4567);
 
         Spark.get("/v1/search", (request, response) -> {
             String id = request.queryParams("id");
-
-            try {
-                int documentId = Integer.parseInt(id);
-                Document document = SqliteReader.retrieveDocumentById(documentId);
-
-                if (document != null) {
-                    Gson gson = new Gson();
-                    String json = gson.toJson(document);
-                    response.type("application/json");
-                    return json;
-                } else {
-                    response.status(404); // Not Found
-                    return "Documento no encontrado para el ID especificado.";
-                }
-            } catch (NumberFormatException e) {
-                response.status(400); // Bad Request
-                return "ID no válido. Debe ser un número entero.";
-            }
-        });
-
-    }
-
-    public void startServerByDocument() {
-        Spark.port(4567);
-
-        Spark.get("/v1/search", (request, response) -> {
             String word = request.queryParams("word");
 
-            try {
-                SqliteReader sqliteReader = new SqliteReader();  // Crea una instancia de la clase SqliteReader
-                List<String> books = sqliteReader.getBooksForWord(word);
+            if (id != null) {
+                // Procesa la búsqueda por ID
+                try {
+                    int documentId = Integer.parseInt(id);
+                    Document document = SqliteReader.retrieveDocumentById(documentId);
 
-                if (!books.isEmpty()) {
-                    List<Document> documents = sqliteReader.getMetadataForBooks(books);
-                    Gson gson = new Gson();
-                    response.type("application/json");
-                    return gson.toJson(documents);
-                } else {
-                    response.status(404); // Not Found
-                    return "Documentos no encontrados para la palabra especificada.";
+                    if (document != null) {
+                        Gson gson = new Gson();
+                        String json = gson.toJson(document);
+                        response.type("application/json");
+                        return json;
+                    } else {
+                        response.status(404); // Not Found
+                        return "Document not found for the specified ID.";
+                    }
+                } catch (NumberFormatException e) {
+                    response.status(400); // Bad Request
+                    return "Invalid ID. It must be an integer.";
                 }
-            } catch (Exception e) {
+            } else if (word != null) {
+                // Procesa la búsqueda por palabra
+                try {
+                    SqliteReader sqliteReader = new SqliteReader();
+                    List<String> books = sqliteReader.getBooksForWord(word);
+
+                    if (!books.isEmpty()) {
[…]

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/SqliteReader.java

@@ -49,7 +49,7 @@ public class SqliteReader {
 
             if (resultSet.next()) {
                 String booksStr = resultSet.getString("book");
-                books = Arrays.asList(booksStr.split(", ")); // Supongamos que los libros están separados por comas
+                books = Arrays.asList(booksStr.split(", "));
             }
         } catch (Exception e) {
             e.printStackTrace();

### 2023-11-05 InverseIndex/Datamart/src/main/java/es/ulpgc/bigdata/inverse_index/datamart/sql/SqlDatamart.java
Implemented SQL datamart

@@ -1,4 +1,61 @@
 package es.ulpgc.bigdata.inverse_index.datamart.sql;
 
-public class SqlDatamart {
+import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
+
+import java.nio.file.Path;
+import java.sql.*;
+import java.util.HashSet;
+import java.util.Set;
+
+public class SqlDatamart implements Datamart {
+	private final Connection conn;
+
+	public SqlDatamart(Path path) throws SQLException {
+		String url =  "jdbc:sqlite:" + path;
+		this.conn = DriverManager.getConnection(url);
+		assertTables();
+	}
+
+	private void assertTables() throws SQLException {
+		// create table
+		Statement stmt = conn.createStatement();
+		stmt.execute("CREATE TABLE IF NOT EXISTS words (" +
+			"word TEXT, " +
+			"book INTEGER" +
+			")"
+		);
+	}
+
+	@Override
+	public Set<Integer> index(String token) throws Exception {
+		Set<Integer> documents = new HashSet<>();
+		PreparedStatement stmt = conn.prepareStatement("SELECT DISTINCT  book FROM words WHERE word = ?");
+		stmt.setString(1, token);
+		ResultSet results = stmt.executeQuery();
+		while (results.next()) {
+			documents.add(results.getInt(1));
+		}
+		return documents;
+	}
+
+	@Override
+	public Set<Integer> documents() throws Exception {
+		Set<Integer> documents = new HashSet<>();
+		Statement stmt = conn.createStatement();
+		ResultSet results = stmt.executeQuery("SELECT DISTINCT book FROM words");
+		while(results.next()) {
+			documents.add(results.getInt(1));
+		}
+		return documents;
+	}
+
+	@Override
+	public void add(int document, Set<String> tokens) throws Exception {
+		PreparedStatement stmt = conn.prepareStatement("INSERT INTO words (word, book) VALUES (?, ?)");
+		for (String token : tokens) {
+			stmt.setString(1, token);
+			stmt.setInt(2, document);
+			stmt.executeUpdate();
+		}
+	}
 }

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/SparkWebService.java
crawler

@@ -14,39 +14,17 @@ public class SparkWebService {
         Spark.port(4567);
 
         Spark.get("/v1/search", (request, response) -> {
-            String id = request.queryParams("id");
             String word = request.queryParams("word");
 
-            if (id != null) {
-                // Procesa la búsqueda por ID
-                try {
-                    int documentId = Integer.parseInt(id);
-                    Document document = SqliteReader.retrieveDocumentById(documentId);
-
-                    if (document != null) {
-                        Gson gson = new Gson();
-                        String json = gson.toJson(document);
-                        response.type("application/json");
-                        return json;
-                    } else {
-                        response.status(404); // Not Found
-                        return "Document not found for the specified ID.";
-                    }
-                } catch (NumberFormatException e) {
-                    response.status(400); // Bad Request
-                    return "Invalid ID. It must be an integer.";
-                }
-            } else if (word != null) {
-                // Procesa la búsqueda por palabra
+            if (word != null) {
                 try {
                     SqliteReader sqliteReader = new SqliteReader();
                     List<String> books = sqliteReader.getBooksForWord(word);
 
                     if (!books.isEmpty()) {
-                        List<Document> documents = sqliteReader.getMetadataForBooks(books);
                         Gson gson = new Gson();
                         response.type("application/json");
-                        return gson.toJson(documents);
+                        return gson.toJson(books);
                     } else {
                         response.status(404); // Not Found
                         return "Documents not found for the specified word.";
@@ -56,7 +34,6 @@ public class SparkWebService {
                     return "Error processing the request: " + e.getMessage();
                 }
             } else {
-                // Manejar caso en el que no se proporciona ni "id" ni "word"
                 response.status(400); // Bad Request
                 return "You must provide either 'id' or 'word' as a query parameter.";
             }

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/SqliteReader.java

@@ -5,107 +5,27 @@ import java.sql.DriverManager;
 import java.sql.PreparedStatement;
 import java.sql.ResultSet;
 import java.util.ArrayList;
-import java.util.Arrays;
 import java.util.List;
-
 
 public class SqliteReader {
 
-
-    public static Document retrieveDocumentById(int id) {
-        Document document = null;
-        String url = "jdbc:sqlite:metadata.db";
-
-        try (Connection connection = DriverManager.getConnection(url);
-             PreparedStatement preparedStatement = connection.prepareStatement("SELECT id, date, author, text, title, lang FROM metadata WHERE id = ?")) {
-            preparedStatement.setInt(1, id);
-            ResultSet resultSet = preparedStatement.executeQuery();
-
-            if (resultSet.next()) {
-                int documentId = resultSet.getInt("id");
-                String date = resultSet.getString("date");
-                String author = resultSet.getString("author");
-                String text = resultSet.getString("text");
-                String title = resultSet.getString("title");
-                String lang = resultSet.getString("lang");
-
-                document = new Document(documentId, date, author, text, title, lang);
-            }
-        } catch (Exception e) {
-            e.printStackTrace();
-        }
-
-        return document;
-    }
-
     public List<String> getBooksForWord(String word) {
         List<String> books = new ArrayList<>();
-        String url = "jdbc:sqlite:metadata.db";
+
+        String url = "jdbc:sqlite:datamart.db";
 
         try (Connection connection = DriverManager.getConnection(url);
-             PreparedStatement preparedStatement = connection.prepareStatement("SELECT word, book FROM words WHERE word = ?")) {
+             PreparedStatement preparedStatement = connection.prepareStatement("SELECT book FROM words WHERE words = ?")) {
             preparedStatement.setString(1, word);
             ResultSet resultSet = preparedStatement.executeQuery();
 
-            if (resultSet.next()) {
-                String booksStr = resultSet.getString("book");
-                books = Arrays.asList(booksStr.split(", "));
+            while (resultSet.next()) {
+                String book = resultSet.getString("book");
+                books.add(book);
             }
         } catch (Exception e) {
             e.printStackTrace();
         }
         return books;
     }
-
-    public List<Document> getMetadataForBooks(List<String> books) {
-        ArrayList<Document> documents = new ArrayList<>();
-        String url = "jdbc:sqlite:metadata.db";
-
-        try (Connection connection = DriverManager.getConnection(url)) {
[…]

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/Document.java
crawler

@@ -1,21 +1,0 @@
-package es.ulpgc.bigdata.inverse_index;
-
-public class Document {
-    private int id;
-    private String date;
-    private String author;
-    private String text;
-    private String title;
-    private String lang;
-
-    public Document(int id, String date, String author, String text, String title, String lang) {
-        this.id = id;
-        this.date = date;
-        this.author = author;
-        this.text = text;
-        this.title = title;
-        this.lang = lang;
-    }
-
-}
-

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/SqliteReader.java

@@ -15,7 +15,7 @@ public class SqliteReader {
         String url = "jdbc:sqlite:datamart.db";
 
         try (Connection connection = DriverManager.getConnection(url);
-             PreparedStatement preparedStatement = connection.prepareStatement("SELECT book FROM words WHERE words = ?")) {
+             PreparedStatement preparedStatement = connection.prepareStatement("SELECT book word FROM words WHERE words = ?")) {
             preparedStatement.setString(1, word);
             ResultSet resultSet = preparedStatement.executeQuery();
 

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/SqliteReader.java
crawler

@@ -15,7 +15,7 @@ public class SqliteReader {
         String url = "jdbc:sqlite:datamart.db";
 
         try (Connection connection = DriverManager.getConnection(url);
-             PreparedStatement preparedStatement = connection.prepareStatement("SELECT book word FROM words WHERE words = ?")) {
+             PreparedStatement preparedStatement = connection.prepareStatement("SELECT book FROM words WHERE word = ?")) {
             preparedStatement.setString(1, word);
             ResultSet resultSet = preparedStatement.executeQuery();
 

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/ContentExtractor.java
Add files via upload

@@ -1,0 +1,46 @@
+package es.ulpgc.bigdata;
+
+import java.io.BufferedReader;
+import java.io.IOException;
+import java.io.InputStreamReader;
+import java.net.HttpURLConnection;
+import java.net.URL;
+
+
+public class ContentExtractor {
+
+    public static String textExtractor(int id) {
+        String url = "https://www.gutenberg.org/cache/epub/" + id + "/pg" + id + ".txt";
+
+        try {
+            URL obj = new URL(url);
+            HttpURLConnection con = (HttpURLConnection) obj.openConnection();
+
+            //HTTP request
+            con.setRequestMethod("GET");
+
+            int responseCode = con.getResponseCode();
+            if (responseCode == HttpURLConnection.HTTP_OK) {
+                BufferedReader in = new BufferedReader(new InputStreamReader(con.getInputStream()));
+                String inputLine;
+                StringBuilder response = new StringBuilder();
+
+                while ((inputLine = in.readLine()) != null) {
+                    response.append(inputLine);
+                    response.append("\n"); //add line breaks to maintain the text format
+                }
+                in.close();
+                return response.toString();
+            }
+            else {
+                System.out.println("An error occurred while retrieving the text from the book " + id + ", response code: " + responseCode);
+                return null;
+            }
+        }
+        catch (IOException e) {
+            System.out.println("Error when trying to obtain the text from the book " + id);
+            e.printStackTrace();
+            return null;
+        }
+    }
+}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/Document.java

@@ -1,0 +1,17 @@
+package es.ulpgc.bigdata;
+
+public class Document {
+    private final String title;
+    private final String author;
+    private final String date;
+    private final String lang;
+    private final String text;
+
+    public Document(String title, String author, String date, String lang, String text) {
+        this.title = title;
+        this.author = author;
+        this.date = date;
+        this.lang = lang;
+        this.text = text;
+    }
+}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/FileSystemDatalake.java

@@ -1,0 +1,60 @@
+package es.ulpgc.bigdata;
+
+import com.google.gson.Gson;
+import com.google.gson.GsonBuilder;
+
+import java.io.*;
+import java.util.Map;
+import java.util.Scanner;
+
+public class FileSystemDatalake {
+    private static File datalakeRoot;
+
+    public FileSystemDatalake(File datalakeRoot) {
+        FileSystemDatalake.datalakeRoot = datalakeRoot;
+        //check if the root directory of the Datalake already exists
+        if (!datalakeRoot.exists()) {
+            //attempt to create the root directory
+            if (FileSystemDatalake.datalakeRoot.mkdirs()) {
+                System.out.println("The Datalake has been successfully created at: " + datalakeRoot.getAbsolutePath());
+            } else {
+                System.out.println("The Datalake could not be created at: " + datalakeRoot.getAbsolutePath());
+            }
+        } else {
+            System.out.println("The Datalake already exists in: " + datalakeRoot.getAbsolutePath());
+        }
+    }
+
+    public static void saveText(int id, String text) {
+        File file = new File(datalakeRoot, id + ".json");
+        try {
+            Map<String, String> dat = LibroGutenberg.transform(id, text);
+            if (dat != null) {
+                File jsonFile = new File(datalakeRoot, id + ".json");
+                if (file.exists()){
+                    try (FileWriter writer = new FileWriter(jsonFile)) {
+                        //converts the data to JSON and write in the file
+                        Gson gson = new GsonBuilder().setPrettyPrinting().create();
+                        String json = gson.toJson(dat);
+                        writer.write(json);
+                        System.out.println("File '"+ id +".json"+"' has been succesfully updated");
+                    }
+                } else{
+                    try (FileWriter writer = new FileWriter(jsonFile)) {
+                        //converts the data to JSON and write in the file
+                        Gson gson = new GsonBuilder().setPrettyPrinting().create();
+                        String json = gson.toJson(dat);
+                        writer.write(json);
+                        System.out.println("Saved '" + id + ".json'");
+                    }
+                }
+
+            } else {
+                System.out.println("It couldn't be saved because the content of the book " + id + " is empty");
+            }
+        } catch (IOException e) {
+            System.out.println("Error while saving " + id + ", with this exception: " + e);
+            e.printStackTrace();
+        }
+    }
+}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/LibroGutenberg.java

@@ -1,0 +1,54 @@
+package es.ulpgc.bigdata;
+import java.util.*;
+import java.util.regex.Matcher;
+import java.util.regex.Pattern;
+
+
+public class LibroGutenberg {
+
+    public static Map<String, String> transform(int id, String text) {
+        //this is a list of tuples where each tuple contains the attribute name and an associated regular expression for searching that attribute in the text
+        List<AbstractMap.SimpleEntry<String, Pattern>> attributes = Arrays.asList(
+                new AbstractMap.SimpleEntry<>("title", Pattern.compile("Title: (.*)", Pattern.CASE_INSENSITIVE)),
+                new AbstractMap.SimpleEntry<>("author", Pattern.compile("(?:Author|Creator|Contributor): (.*)", Pattern.CASE_INSENSITIVE)),
+                new AbstractMap.SimpleEntry<>("date", Pattern.compile("Release date: (.*)", Pattern.CASE_INSENSITIVE)),
+                new AbstractMap.SimpleEntry<>("lang", Pattern.compile("Language: (.*)", Pattern.CASE_INSENSITIVE))
+        );
+
+        //these are regular expressions that search for the start and end marks of the book within the text.
+        //these marks have the format "*** START OF ... " and "END OF ... ***," are used to delimit the main content of the book.
+        Pattern startPattern = Pattern.compile("(\\*\\*\\* START OF (THE|THIS) PROJECT GUTENBERG EBOOK.*?\\*\\*\\*)");
+        Pattern endPattern = Pattern.compile("(\\*\\*\\* END OF (THE|THIS) PROJECT GUTENBERG EBOOK.*?\\*\\*\\*)");
+
+        Map<String, String> data = new HashMap<>();
+
+        try {
+            for (AbstractMap.SimpleEntry<String, Pattern> attribute : attributes) {
+                Matcher matcher = attribute.getValue().matcher(text);
+                if (matcher.find()) {
+                    data.put(attribute.getKey(), matcher.group(1));
+                } else {
+                    System.out.println("Couldn't parse " + attribute.getKey() + " for " + id);
+                }
+            }
+
+            Matcher startMatcher = startPattern.matcher(text);
+            Matcher endMatcher = endPattern.matcher(text);
+
+            if (startMatcher.find() && endMatcher.find()) {
+                String bookText = text.substring(startMatcher.end(), endMatcher.start());
+                data.put("text", bookText);
+            } else {
+                System.out.println("Error parsing text for " + id);
[…]

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/Main.java

@@ -1,0 +1,24 @@
+package es.ulpgc.bigdata;
+
+import java.io.File;
+
+
+import java.io.File;
+
+import static java.lang.Thread.sleep;
+import static spark.Spark.init;
+import static spark.Spark.port;
+
+public class Main {
+    public static void main(String[] args) throws InterruptedException {
+        port(4567);
+        TimerAPI.setupTimerAPI();
+        init();
+
+        File datalakeRoot = new File(args[0]);
+        Controller controller = new Controller(datalakeRoot);
+        controller.start();
+
+    }
+}
+

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Datamart/src/main/java/es/ulpgc/bigdata/inverse_index/datamart/Datamart.java

@@ -1,0 +1,9 @@
+package es.ulpgc.bigdata.inverse_index.datamart;
+
+import java.util.Set;
+
+public interface Datamart {
+	Set<Integer> index(String token) throws Exception;
+	Set<Integer> documents() throws Exception;
+	void add(int document, Set<String> tokens) throws Exception;
+}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Datamart/src/main/java/es/ulpgc/bigdata/inverse_index/datamart/file/FileDatamart.java

@@ -1,0 +1,104 @@
+package es.ulpgc.bigdata.inverse_index.datamart.file;
+
+import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
+
+import java.io.IOException;
+import java.nio.file.Files;
+import java.nio.file.Path;
+import java.util.HashSet;
+import java.util.Set;
+
+public class FileDatamart implements Datamart {
+	private final Path root;
+
+	public FileDatamart(Path root) throws IOException {
+		this.root = root;
+
+		if (Files.exists(root)) {
+			// The root already exists, assert that it's a directory and follows the format specified
+			if (!Files.isDirectory(root)) {
+				throw new IllegalArgumentException("The root must be a directory");
+			}
+		} else {
+			// The root doesn't exist, create it
+			Files.createDirectories(root);
+		}
+	}
+
+	private Path assertWord (String word) throws Exception {
+		//TODO: handle edge cases
+		String beginning = word.substring(0, 2);
+		Path neighbourDir = root.resolve(beginning);
+		if (!Files.isDirectory(neighbourDir)) {
+			if (Files.exists(neighbourDir)) {
+				throw new Exception("Unexpected file in datamart " + neighbourDir);
+			}
+			Files.createDirectory(neighbourDir);
+		}
+		Path wordFile = neighbourDir.resolve(word);
+		if (!Files.isRegularFile(wordFile)) {
+			if (Files.exists(wordFile)) {
+				throw new Exception("Unexpected non file in datamart " + wordFile);
+			}
+			Files.createFile(wordFile);
+		}
+
+		return wordFile;
+	}
+
+	private Set<Integer> readWordFile(Path wordFile) throws IOException {
+		byte[] content = Files.readAllBytes(wordFile);
+		Set<Integer> documents = new HashSet<>();
+		for (int i = 0; i < content.length; i += 4) {
+			documents.add(byteToInt(content, i));
+		}
+		return documents;
+	}
+
+	private int byteToInt(byte[] bytes, int offset) {
+		return (bytes[offset] << 24) | (bytes[offset + 1] << 16) | (bytes[offset + 2] << 8) | bytes[offset + 3];
+	}
+
+	@Override
+	public Set<Integer> index(String token) throws Exception {
+		Path wordFile = assertWord(token);
+		return readWordFile(wordFile);
+	}
+
+	@Override
+	public Set<Integer> documents() throws IOException {
[…]

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Datamart/src/main/java/es/ulpgc/bigdata/inverse_index/datamart/sql/SqlDatamart.java

@@ -1,0 +1,61 @@
+package es.ulpgc.bigdata.inverse_index.datamart.sql;
+
+import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
+
+import java.nio.file.Path;
+import java.sql.*;
+import java.util.HashSet;
+import java.util.Set;
+
+public class SqlDatamart implements Datamart {
+	private final Connection conn;
+
+	public SqlDatamart(Path path) throws SQLException {
+		String url =  "jdbc:sqlite:" + path;
+		this.conn = DriverManager.getConnection(url);
+		assertTables();
+	}
+
+	private void assertTables() throws SQLException {
+		// create table
+		Statement stmt = conn.createStatement();
+		stmt.execute("CREATE TABLE IF NOT EXISTS words (" +
+			"word TEXT, " +
+			"book INTEGER" +
+			")"
+		);
+	}
+
+	@Override
+	public Set<Integer> index(String token) throws Exception {
+		Set<Integer> documents = new HashSet<>();
+		PreparedStatement stmt = conn.prepareStatement("SELECT DISTINCT  book FROM words WHERE word = ?");
+		stmt.setString(1, token);
+		ResultSet results = stmt.executeQuery();
+		while (results.next()) {
+			documents.add(results.getInt(1));
+		}
+		return documents;
+	}
+
+	@Override
+	public Set<Integer> documents() throws Exception {
+		Set<Integer> documents = new HashSet<>();
+		Statement stmt = conn.createStatement();
+		ResultSet results = stmt.executeQuery("SELECT DISTINCT book FROM words");
+		while(results.next()) {
+			documents.add(results.getInt(1));
+		}
+		return documents;
+	}
+
+	@Override
+	public void add(int document, Set<String> tokens) throws Exception {
+		PreparedStatement stmt = conn.prepareStatement("INSERT INTO words (word, book) VALUES (?, ?)");
+		for (String token : tokens) {
+			stmt.setString(1, token);
+			stmt.setInt(2, document);
+			stmt.executeUpdate();
+		}
+	}
+}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/FileDatalake.java

@@ -1,0 +1,60 @@
+package es.ulpgc.bigdata.inverse_index.indexer;
+
+import com.google.gson.Gson;
+import com.google.gson.JsonObject;
+
+import java.io.IOException;
+import java.nio.file.Files;
+import java.nio.file.Path;
+import java.nio.file.WatchKey;
+import java.nio.file.WatchService;
+import java.util.HashSet;
+import java.util.Set;
+import java.util.function.BiConsumer;
+import java.util.function.Predicate;
+import java.util.regex.Pattern;
+
+public class FileDatalake {
+	private final Path root;
+
+	public FileDatalake(Path root) {
+		this.root = root;
+	}
+
+
+	public Set<Integer> documents() throws IOException {
+		Set<Integer> documents = new HashSet<>();
+		Predicate<String> isDocument = Pattern.compile("\\d+\\.json").asMatchPredicate();
+		for (Path document: Files.list(root).toList()) {
+			if (!Files.isRegularFile(document)) continue;
+			String name = document.getFileName().toString();
+			if (!isDocument.test(name)) continue;
+			documents.add(Integer.parseInt(name.split("\\.")[0]));
+		}
+		return documents;
+	}
+
+	public String readDocument(int document) throws IOException {
+		Gson gson = new Gson();
+		JsonObject el = gson.fromJson(Files.readString(root.resolve(document + ".json")), JsonObject.class);
+		return el.get("text").getAsString();
+	}
+
+	public void blockAndListen(BiConsumer<Integer, String> documentConsumer) throws IOException, InterruptedException {
+		WatchService ws = root.getFileSystem().newWatchService();
+		root.register(ws, java.nio.file.StandardWatchEventKinds.ENTRY_MODIFY);
+		for (;;) {
+			WatchKey key = ws.take();
+			for (var event : key.pollEvents()) {
+				String name = event.context().toString();
+				if (!Pattern.compile("\\d+\\.json").asMatchPredicate().test(name)) continue;
+				int document = Integer.parseInt(name.split("\\.")[0]);
+				documentConsumer.accept(document, readDocument(document));
+			}
+			boolean valid = key.reset();
+			if (!valid) {
+				break;
+			}
+		}
+	}
+}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/Indexer.java

@@ -1,0 +1,113 @@
+package es.ulpgc.bigdata.inverse_index.indexer;
+
+import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
+
+import java.io.IOException;
+import java.util.HashSet;
+import java.util.Set;
+import java.util.function.BiConsumer;
+import java.util.function.Predicate;
+
+public class Indexer {
+	private static final int MAX_TOKEN_LENGTH = 20;
+	private static final Set<Character> PUNCTUATION_SET = Set.of('.', ',', ';', ':', '?', '!', '¡', '¿', '(', ')', '*', '"');
+	private static final Set<Character> TOKEN_INNER_CHAR_SET = Set.of('\'', '-', '_');
+
+	private final FileDatalake datalake;
+	private final Datamart datamart;
+
+	public Indexer(FileDatalake datalake, Datamart datamart) {
+		this.datalake = datalake;
+		this.datamart = datamart;
+	}
+
+	public static Set<String> tokenize(String document) {
+		Set<String> tokens = new HashSet<>();
+		int currTokenStart = 0;
+		int safeTokenEnd = 0;
+		IndexerState state = IndexerState.OutOfToken;
+
+		Predicate<Character> isWhitespaceOrPunctuation = c -> Character.isWhitespace(c) || PUNCTUATION_SET.contains(c);
+		Predicate<Character> isTokenCharacter = c -> Character.isLetter(c) || Character.isDigit(c);
+
+		BiConsumer<Integer, Integer> addToken = (start, end) -> tokens.add(document.substring(start, end).toLowerCase());
+
+		for (int i = 0; i < document.length(); i++) {
+			char c = document.charAt(i);
+			int tokenLength = i - currTokenStart;
+			switch (state) {
+				case OutOfToken:
+					if (isTokenCharacter.test(c)) {
+						state = IndexerState.InToken;
+					} else if (isWhitespaceOrPunctuation.test(c) || TOKEN_INNER_CHAR_SET.contains(c)) {
+						currTokenStart = i + 1;
+					}
+					break;
+				case InToken:
+					// the last character was valid for a token, so the current index would be a safe end.
+					safeTokenEnd = i;
+					if (tokenLength > MAX_TOKEN_LENGTH) {
+						state = IndexerState.InInvalidToken;
+					}
+					if (isWhitespaceOrPunctuation.test(c)) {
+						state = IndexerState.OutOfToken;
+						addToken.accept(currTokenStart, safeTokenEnd);
[…]

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Indexer/src/test/java/es/ulpgc/bigdata/inverse_index/IndexerTest.java

@@ -1,0 +1,52 @@
+package es.ulpgc.bigdata.inverse_index;
+
+import es.ulpgc.bigdata.inverse_index.indexer.Indexer;
+import org.junit.jupiter.api.Test;
+
+import java.util.Set;
+
+import static org.junit.jupiter.api.Assertions.*;
+
+class IndexerTest {
+		@Test
+		void indexbasic() {
+			String text = "This is a test!";
+			Set<String> tokens = Indexer.tokenize(text);
+			assertEquals(Set.of("this", "is", "a", "test"), tokens);
+		}
+
+		@Test
+		void indexDash() {
+			String text = "This is a test-test!";
+			Set<String> tokens = Indexer.tokenize(text);
+			assertEquals(Set.of("this", "is", "a", "test-test"), tokens);
+		}
+
+		@Test
+		void indexUnderscorePrefixPostfix() {
+			String text = "This is a test_ _test";
+			Set<String> tokens = Indexer.tokenize(text);
+			assertEquals(Set.of("this", "is", "a", "test"), tokens);
+		}
+
+		@Test
+	void indexLotsOfWhitespace() {
+		String text = "This is a test!   \n\n\nnew line!";
+		Set<String> tokens = Indexer.tokenize(text);
+		assertEquals(Set.of("this", "is", "a", "test", "new", "line"), tokens);
+		}
+
+		@Test
+		void indexNumbers() {
+			String text = "1234 7777 23";
+			Set<String> tokens = Indexer.tokenize(text);
+			assertEquals(Set.of("1234", "7777", "23"), tokens);
+		}
+
+		@Test
+		void indexTooLongToken() {
+			String text = "short _long123456789123456789_ after other________________________________long";
+			Set<String> tokens = Indexer.tokenize(text);
+			assertEquals(Set.of("short", "after"), tokens);
+		}
+}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/Controller.java

@@ -1,0 +1,11 @@
+package es.ulpgc.bigdata.inverse_index;
+
+
+
+
+public class Controller {
+    public void startServers() {
+        SparkWebService sparkWebService = new SparkWebService();
+        sparkWebService.startServer();
+    }
+}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/Main.java

@@ -1,0 +1,7 @@
+package es.ulpgc.bigdata.inverse_index;
+
+public class Main {
+	public static void main(String[] args) {
+		new Controller().startServers();
+	}
+}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/SparkWebService.java

@@ -1,0 +1,42 @@
+package es.ulpgc.bigdata.inverse_index;
+
+
+
+
+import com.google.gson.Gson;
+import spark.Spark;
+
+import java.util.List;
+
+public class SparkWebService {
+
+    public void startServer() {
+        Spark.port(4567);
+
+        Spark.get("/v1/search", (request, response) -> {
+            String word = request.queryParams("word");
+
+            if (word != null) {
+                try {
+                    SqliteReader sqliteReader = new SqliteReader();
+                    List<String> books = sqliteReader.getBooksForWord(word);
+
+                    if (!books.isEmpty()) {
+                        Gson gson = new Gson();
+                        response.type("application/json");
+                        return gson.toJson(books);
+                    } else {
+                        response.status(404); // Not Found
+                        return "Documents not found for the specified word.";
+                    }
+                } catch (Exception e) {
+                    response.status(400); // Bad Request
+                    return "Error processing the request: " + e.getMessage();
+                }
+            } else {
+                response.status(400); // Bad Request
+                return "You must provide either 'id' or 'word' as a query parameter.";
+            }
+        });
+    }
+}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/SqliteReader.java

@@ -1,0 +1,31 @@
+package es.ulpgc.bigdata.inverse_index;
+
+import java.sql.Connection;
+import java.sql.DriverManager;
+import java.sql.PreparedStatement;
+import java.sql.ResultSet;
+import java.util.ArrayList;
+import java.util.List;
+
+public class SqliteReader {
+
+    public List<String> getBooksForWord(String word) {
+        List<String> books = new ArrayList<>();
+
+        String url = "jdbc:sqlite:datamart.db";
+
+        try (Connection connection = DriverManager.getConnection(url);
+             PreparedStatement preparedStatement = connection.prepareStatement("SELECT book FROM words WHERE word = ?")) {
+            preparedStatement.setString(1, word);
+            ResultSet resultSet = preparedStatement.executeQuery();
+
+            while (resultSet.next()) {
+                String book = resultSet.getString("book");
+                books.add(book);
+            }
+        } catch (Exception e) {
+            e.printStackTrace();
+        }
+        return books;
+    }
+}

### 2023-11-05 inverse-index-big-data-main/indexer/indexer_commons.py

@@ -1,0 +1,55 @@
+import json
+import os
+import sqlite3
+from tqdm import tqdm
+
+def document_generator(datalake):
+	books = os.listdir(datalake)
+	for book in tqdm(books):
+		# Combinamos la ruta completa con el nombre del archivo
+		archivo = os.path.join(datalake, book)
+
+		# Verificamos si el archivo es un archivo JSON
+		if book.endswith('.json'):
+			doc_id = int(book[:-5])
+			with open(archivo, 'r', encoding='utf-8') as archivo_json:
+				yield doc_id, json.load(archivo_json)
+
+def create_datamart(datalake_dir, datamart_path, index):
+	conn = sqlite3.connect(datamart_path)
+	c = conn.cursor()
+
+	# Crear la tabla "words" con dos columnas: palabra y lista de libros
+	c.execute("""
+		CREATE TABLE IF NOT EXISTS inv_index (
+		word TEXT,
+		doc_id INTEGER
+	)""")
+
+	c.execute("""
+		CREATE TABLE IF NOT EXISTS documents (
+		id INTEGER,
+		title TEXT,
+		date TEXT,
+		content TEXT
+	)""")
+
+	for word, docs in index.items():
+		for doc in docs:
+			c.execute("""
+					INSERT OR REPLACE INTO inv_index (word, doc_id) VALUES (?, ?)
+				""",
+				(word, doc)
+			)
+
+	for doc_id, doc in document_generator(datalake_dir):
+		c.execute(
+			"""INSERT OR REPLACE INTO documents (id, title, date, content)
+			VALUES (?, ?, ?, ?)
+			""",
+			(doc_id, doc.get("title"), doc.get("date"), doc.get("text"))
+		)
+
+	conn.commit()
+	conn.close()
+

### 2023-11-05 inverse-index-big-data-main/indexer/nltk_indexer.py

@@ -1,0 +1,36 @@
+import sys
+import nltk
+from collections import defaultdict
+from indexer_commons import document_generator, create_datamart
+
+def indexer(document_list):
+	"""
+	Creates an inverted word index based on a list of documents.
+	Args:
+		document_list (generator): A generator of tuples (doc_id, document), where
+			doc_id is the document identifier, and document is a dictionary containing
+			a 'text' key with the document's text.
+	Returns:
+		defaultdict: The inverted word index where keys are words, and values are sets
+		of document identifiers containing that word.
+	"""
+	index = defaultdict(set)
+	for doc_id, document in document_list:
+		text = document["text"]
+		# Tokenize the text into words using NLTK
+		words = set(nltk.word_tokenize(text))
+		for word in words:
+			index[word].add(doc_id)
+	return index
+
+if __name__ == "__main__":
+	if len(sys.argv) < 3:
+		print("Usage: python nltk_indexer.py <datalake> <datamart>")
+		exit(1)
+	# Ścieżka do katalogu z plikami JSON
+	datalake_path = sys.argv[1]
+
+	index = indexer(document_generator(datalake_path))
+
+	datamart_path = sys.argv[2]
+	create_datamart(datalake_path, datamart_path, index)

### 2023-11-05 inverse-index-big-data-main/indexer/spacy_indexer.py

@@ -1,0 +1,42 @@
+##Se instala el spacy y el en_core_web_sm
+import json
+import os
+import sys
+import spacy  
+from tqdm import tqdm
+from collections import defaultdict
+
+from indexer_commons import document_generator, create_datamart
+
+def indexer(documents):
+	reverse_index = defaultdict(set)
+	for doc_id, document in documents:
+		texto = document.get("text")
+		texto_sobrante = texto
+
+		while len(texto_sobrante) > 0:
+			if len(texto_sobrante) > 1_000_000:
+				candidato = texto_sobrante[:1_000_000]
+				index = candidato.rfind(" ")
+				texto_seccion = texto_sobrante[:index]
+				texto_sobrante = texto_sobrante[index:]
+			else:
+				texto_seccion, texto_sobrante = texto_sobrante, ""
+
+			nlp = spacy.load("en_core_web_sm")
+			doc = nlp(texto_seccion) # Crea un objeto de spacy tipo nlp
+			lexical_tokens = [t.orth_ for t in doc if not (t.is_punct or t.is_stop)]
+			unique_tokens = set(lexical_tokens)
+
+			for word in unique_tokens:
+				reverse_index[word].add(doc_id)
+	return reverse_index
+
+if __name__ == "__main__":
+	if len(sys.argv) < 3:
+		print("Usage: python spacy_index.py <datalake> <datamart>")
+		exit(1)
+	datalake_dir = sys.argv[1]
+	index = indexer(document_generator(datalake_dir))
+	datamart_path = sys.argv[2]
+	create_datamart(datalake_dir, datamart_path, index)

### 2023-11-05 inverse-index-big-data-main/scraper/scraper.py

@@ -1,0 +1,74 @@
+import sys
+import os
+import json
+import re
+import asyncio
+import aiohttp
+
+if len(sys.argv) < 2:
+	print("Usage: python3 scraper.py <datalake>")
+	exit(1)
+
+datalake_dir = sys.argv[1]
+
+os.makedirs(datalake_dir, exist_ok=True)
+
+def transform(id, text: str) -> str:
+	attributes = [
+		("title", re.compile(r"Title: (.*)", flags=re.IGNORECASE)),
+		("author", re.compile(r"(?:Author|Creator|Contributor): (.*)", flags=re.IGNORECASE)),
+		("date", re.compile(r"Release date: (.*)", flags=re.IGNORECASE)),
+		("lang", re.compile(r"Language: (.*)", flags=re.IGNORECASE))
+	]
+	start_re = re.compile(r"(\*\*\* START OF (THE|THIS) PROJECT GUTENBERG EBOOK.*?\*\*\*)")
+	end_re = re.compile(r"(\*\*\* END OF (THE|THIS) PROJECT GUTENBERG EBOOK.*?\*\*\*)")
+	data = {}
+	try:
+		for attr_name, attr_re in attributes:
+			m = attr_re.search(text)
+			if m:
+				data[attr_name] = m.group(1)
+			else :
+				print(f"Couldn't parse {attr_name} for {id}")
+		start_m = start_re.search(text)
+		end_m = end_re.search(text)
+		if not (start_m and end_m):
+			# this happens, for example, in doc 673
+			return None
+		data["text"] = text[start_m.end():end_m.start()]
+	except AttributeError as e:
+		print(f"Error parsing text for {id}")
+		print(e)
+		exit(1)
+	return data
+
+
+async def fetch(session, id):
+	async with session.get(f"https://www.gutenberg.org/cache/epub/{id}/pg{id}.txt") as response:
+		return (await response.text(), response.status)
+
+async def save_text(session, id):
+		text, status = await fetch(session, id)
+		if status != 200:
+			print(f"{id} could not be fetched")
+			return
+
+		text = text.replace("\r\n", "\n")
+		dat = transform(id, text)
+		if dat is None:
+			print(f"{id} is not a document")
+			return
+
+		with open(os.path.join(datalake_dir, f"{id}.json"), "w") as f:
+			json.dump(dat, f)
+		print(f"Saved {id}")
+
+async def main():
+	async with aiohttp.ClientSession() as session:
[…]

### 2023-11-05 latexJava/paperJava.tex
update paperJava.tex

@@
 Our code encompasses three concurrent modules: Crawler, Indexer and QueryEngine, all working in unison to ensure seamless operation.
-To ensure optimal performance, we integrated a timer mechanism that defaults to downloading 100 books per minute.
-%To accomplish this task, we followed these steps:
-%we collected a hundred English books, tokenized them to split them into words, built an inverted index that could relate these terms to the specific ID of each book, and developed a series of tables that allowed us to associate both the tokenized words with the IDs and these IDs with the metadata specific to each book.
-%tu dodac co porownujemy i co lepsze
+To accomplish this task, we followed these steps: we retrieved and collected digital documents, then processed and indexed these documents for efficient search, and provided a user-friendly interface for searching and retrieving specific documents within the extensive digital library.
+%tu dodac co porownujemy i conslusions
 }
@@
 The 'crawler' module is responsible for retrieving, processing, and storing textual content from books available on the Gutenberg.org website.
-It systematically downloads and handles book content, ensuring that these texts are integrated seamlessly into the inverted index.
+It ensures that these texts are integrated seamlessly into the inverted index.
+Furthermore, the 'Query Engine' module enables searching for and retrieving specific books within this extensive digital library.
+The harmonious synergy of three modules addresses the challenge of efficiently accessing and exploring an ever-expanding collection of digital documents.
 
@@
 
-First, we
+Our project follows a systematic approach, divided into three major modules: the Crawler, Inverted Index and Query Engine.
+First, we employ a data collection program within the Crawler module to download documents from the Gutenberg Project.
+Then, in the Inverted Index module, we process these documents by tokenization, creating a reverse keyword index.
+Subsequently, the Query Engine module provides a user-friendly interface for searching and retrieving specific documents.
+Finally, we store the indexed data in an SQLite database for future querying.
 
@@
 \end{itemize}
-The complete workflow of the "crawler" module can be summarized as follows:
-
-1. Parameters for the download frequency, books per minute, and the maximum number of books to retrieve are configured using the \texttt{TimerAPI} class.
-
-2.
-The main \texttt{Main} class initializes the entire system.
+Finally The main \texttt{Main} class initializes the entire system.
 It sets the port for the system, initializes the Spark server, and passes the location of the Datalake directory to the \texttt{Controller} class.
 
-3.
-The \texttt{Controller} class takes charge of initiating the process of downloading book texts.
-The process is repetitive and continues until the maximum number of books is reached or other predefined termination criteria are met.
+\subsection{Indexer}
 
-4.
-The \texttt{ContentExtractor} class is employed to retrieve textual content from specific books, while the \texttt{LibroGutenberg} class handles the subsequent processing of the text, extracting valuable attributes.
+The Inverted Index module is essential for creating and managing inverted indices based on available textual documents.
+This module plays a crucial role in information retrieval, text analysis, and natural language processing tasks.
 
-5.
-The \texttt{FileSystemDatalake} class manages the storage of the downloaded text in JSON format.
-It is responsible for creating a structured directory hierarchy, facilitating efficient data storage.
+\begin{itemize}
+\item
+The \texttt{FileDatalake} class represents access to the source of textual data stored as files. 
+\begin{itemize}
+\item Function \texttt{documents()} returns a set of document identifiers available in the data source.
+\item  Function \texttt{readDocument(int document)} reads the text content of a specific document based on its identifier.
+\end{itemize}
 
-The "crawler" module serves as a vital component within the system, enabling the retrieval, structured processing, and organized storage of textual content from the Gutenberg.org website.
-This content can subsequently be accessed and utilized in various ways, making it a versatile and valuable module for data acquisition and management.
+\item 
+The \texttt{IndexerState} enumeration defines various states that may occur during the tokenization of a document's text.
+States such as \textit{InToken}, \textit{InInvalidTokenUnknownEnd}, \textit{InInvalidToken}, and \textit{OutOfToken} describe different tokenization scenarios.
 
-\subsection{Indexer}
+\item
+The \texttt{Indexer} class is responsible for creating an inverted index based on documents stored in the \texttt{FileDatalake} and storing it in the \texttt{Datamart}.
+The class provides the following functionalities:
+
+\begin{itemize}
+  \item \texttt{tokenize(String document)}: Tokenizes the text content of a document, splitting it into individual words (tokens), removing punctuation, and preparing tokens for indexing.
+  \item \texttt{index()}: Initiates the indexing process. It creates an inverted index from the available documents in the \texttt{FileDatalake} and stores it in the \texttt{Datamart}.
+\end{itemize}
+
+\item
+The \texttt{IndexerTest} class contains a set of unit tests for the \texttt{Indexer} class.
+These tests verify the correct behavior of the \texttt{tokenize} method in various scenarios (such as checking if it copes with underscores  at the beginning or at the end of words), ensuring the accuracy of tokenization.
+\end{itemize}
+
+Finally the \texttt{Main} class serves as the entry point for the program.
+It accepts two command-line arguments: the path to the \texttt{datalake} (data source) and \texttt{datamart} (destination for the inverted index).
+The program creates instances of \texttt{FileDatalake} and \texttt{Datamart} and then initiates the indexing process using the \texttt{Indexer} class.
+
 \subsection{Query Engine}
+
+The Query Engine module is responsible for providing an API interface and search functionality for indexed documents.
+This section provides an overview of the key classes and their interactions within the Query Engine module.
+
+\begin{itemize}
+\item
+The \texttt{Controller} class serves as the controller in the Query Engine module.
+It is responsible for initializing and running a server that handles client requests.
+The \texttt{Controller} class invokes the \texttt{startServer} method of the \texttt{SparkWebService} object.
+
+\item
+The \texttt{SparkWebService} class utilizes the Spark library to launch an HTTP server.
+This server listens on a specified port and handles HTTP requests, particularly GET requests.
+It provides a single main query, \texttt{/v1/search}, allowing users to search for documents based on keywords.
+
+\item
+The \texttt{SqliteReader} class is responsible for communication with the SQLite database, which stores information about keyword indexes within documents.
+When the server receives a request with a keyword, the \texttt{SqliteReader} extracts information about the documents containing that keyword from the database.
+
+\item 
+The \texttt{Document} class represents an individual textual document. It includes information such as document ID, date, author, content, title, and language.
+\end{itemize}
+
+The \texttt{Main} class contains the \texttt{main} function, which serves as the entry point for the Query Engine module.
+It primarily initializes a \texttt{Controller} object and starts the API server.
+
+The collaboration among these classes is as follows: The Spark server listens for search requests and, upon receiving a query, forwards it to the \texttt{SqliteReader}.
+The \texttt{SqliteReader} communicates with the SQLite database to retrieve documents containing the specified keyword.
+The results are processed and returned to the client in JSON format via the Spark server.
+This allows users to search for documents based on keywords and receive results efficiently.
 

### 2023-11-05 InverseIndex/Datamart/src/main/java/es/ulpgc/bigdata/inverse_index/datamart/file/FileDatamart.java
Worked on improving datamart, cleaned up repo

@@ -11,6 +11,9 @@ import java.util.Set;
 public class FileDatamart implements Datamart {
 	private final Path root;
 
+	private static final int SHORT_LENGTH = 3;
+	private static final String SHORT_DIR = "short";
+
 	public FileDatamart(Path root) throws IOException {
 		this.root = root;
 
@@ -26,9 +29,13 @@ public class FileDatamart implements Datamart {
 	}
 
 	private Path assertWord (String word) throws Exception {
-		//TODO: handle edge cases
-		String beginning = word.substring(0, 2);
-		Path neighbourDir = root.resolve(beginning);
+		Path neighbourDir;
+		if (word.length() <= SHORT_LENGTH) {
+			neighbourDir = root.resolve(SHORT_DIR);
+		} else {
+			String beginning = word.substring(0, 2);
+			neighbourDir = root.resolve(beginning);
+		}
 		if (!Files.isDirectory(neighbourDir)) {
 			if (Files.exists(neighbourDir)) {
 				throw new Exception("Unexpected file in datamart " + neighbourDir);
@@ -42,7 +49,6 @@ public class FileDatamart implements Datamart {
 			}
 			Files.createFile(wordFile);
 		}
-
 		return wordFile;
 	}
 

### 2023-11-05 InverseIndex/Datamart/src/main/java/es/ulpgc/bigdata/inverse_index/datamart/sql/SqlDatamart.java

@@ -14,6 +14,7 @@ public class SqlDatamart implements Datamart {
 		String url =  "jdbc:sqlite:" + path;
 		this.conn = DriverManager.getConnection(url);
 		assertTables();
+		conn.setAutoCommit(false);
 	}
 
 	private void assertTables() throws SQLException {
@@ -57,5 +58,6 @@ public class SqlDatamart implements Datamart {
 			stmt.setInt(2, document);
 			stmt.executeUpdate();
 		}
+		stmt.close();
 	}
 }

### 2023-11-05 InverseIndex/DatamartTest/src/main/java/dbManager/CreateTable.java

@@ -1,77 +1,0 @@
-package dbManager;
-
-import objects.Book;
-
-import java.sql.*;
-
-public class CreateTable {
-
-    public CreateTable() {
-        try (Connection conn = connect()) {
-            Statement statement = conn.createStatement();
-            createMetaDataTable(statement);
-            createWordsTable(statement);
-        } catch (SQLException e) {
-            throw new RuntimeException(e);
-        }
-    }
-
-    public void createMetaDataTable(Statement statement) throws SQLException {
-        statement.execute("CREATE TABLE IF NOT EXISTS metadata (" +
-                "id INTEGER PRIMARY KEY, " +
-                "date TEXT, " +
-                "author TEXT, " +
-                "text TEXT," +
-                "title TEXT," +
-                "lang TEXT" +
-                ")");
-    }
-
-    public void createWordsTable(Statement statement) throws SQLException {
-        statement.execute("CREATE TABLE IF NOT EXISTS words (" +
-                "word TEXT, " +
-                "book TEXT" +
-                ")");
-    }
-
-
-    public void insertWordsTable(String word, String book) {
-        String sql = "INSERT INTO words(word,book) VALUES(?,?)";
-        try (Connection conn = connect();
-             PreparedStatement pstmt = conn.prepareStatement(sql)) {
-            pstmt.setString(1, word);
-            pstmt.setString(2, book);
-            pstmt.executeUpdate();
-        } catch (SQLException e) {
-            System.out.println(e.getMessage());
-        }
-    }
-
-
-    public void insertBookTable(Book book) {
-        String sql = "INSERT INTO metadata(id,date,author,text,title,lang) VALUES(?,?,?,?,?,?)";
-        try (Connection conn = connect();
-             PreparedStatement pstmt = conn.prepareStatement(sql)) {
-            pstmt.setInt(1, book.id());
-            pstmt.setString(2, book.date());
-            pstmt.setString(3, book.author());
-            pstmt.setString(4, book.text());
-            pstmt.setString(5, book.title());
-            pstmt.setString(6, book.lang());
-            pstmt.executeUpdate();
-        } catch (SQLException e) {
-            System.out.println(e.getMessage());
-        }
-    }
-
-    public Connection connect() {
-        Connection conn;
-        try {
-            String url = "jdbc:sqlite:metadata.db/";
-            conn = DriverManager.getConnection(url);
-        } catch (SQLException e) {
-            throw new RuntimeException(e);
-        }
-        return conn;
-    }
-}

### 2023-11-05 InverseIndex/DatamartTest/src/main/java/dbManager/DropTable.java

@@ -1,41 +1,0 @@
-package dbManager;
-
-import java.sql.Connection;
-import java.sql.DriverManager;
-import java.sql.SQLException;
-import java.sql.Statement;
-
-public class DropTable {
-
-    public DropTable() {
-        try (Connection conn = connect()) {
-            Statement statement = conn.createStatement();
-            dropMetaDataTable(statement);
-            dropWordsTable(statement);
-
-        } catch (SQLException e) {
-            throw new RuntimeException(e);
-        }
-    }
-
-    public void dropMetaDataTable(Statement statement) throws SQLException {
-        statement.execute("DROP TABLE IF EXISTS metadata;");
-        System.out.println("Table dropped");
-    }
-    public void dropWordsTable(Statement statement) throws SQLException {
-        statement.execute("DROP TABLE IF EXISTS words;");
-        System.out.println("Table dropped");
-    }
-
-
-    public Connection connect() {
-        Connection conn;
-        try {
-            String url = "jdbc:sqlite:metadata.db/";
-            conn = DriverManager.getConnection(url);
-        } catch (SQLException e) {
-            throw new RuntimeException(e);
-        }
-        return conn;
-    }
-}

### 2023-11-05 InverseIndex/DatamartTest/src/main/java/objects/Book.java

@@ -1,33 +1,0 @@
-package objects;
-
-public record Book(Integer id, String date, String author, String text, String title, String lang){
-
-    @Override
-    public Integer id() {
-        return id;
-    }
-    @Override
-    public String date() {
-        return date;
-    }
-
-    @Override
-    public String author() {
-        return author;
-    }
-
-    @Override
-    public String text() {
-        return text;
-    }
-
-    @Override
-    public String title() {
-        return title;
-    }
-
-    @Override
-    public String lang() {
-        return lang;
-    }
-}

### 2023-11-05 InverseIndex/DatamartTest/src/main/java/org/example/DatamartController.java

@@ -1,24 +1,0 @@
-package org.example;
-
-import dbManager.DropTable;
-
-import java.io.File;
-
-public class DatamartController {
-
-    private final MetadataExtractor metadataCall = new MetadataExtractor();
-    private final WordsExtractor wordsCall = new WordsExtractor();
-    public void run(File datalake) {
-        if (datalake.exists() && datalake.isDirectory()) {
-            new MetadataExtractor().filter(datalake);
-            new DropTable();
-            metadataCall.filter(datalake);
-            wordsCall.filter();
-
-        } else {
-            System.out.println("The directory is not valid or not exists.");
-
-        }
-
-    }
-}

### 2023-11-05 InverseIndex/DatamartTest/src/main/java/org/example/Main.java

@@ -1,12 +1,0 @@
-package org.example;
-
-import java.io.File;
-
-public class Main {
-    public static void main(String[] args) {
-        File datalake = new File(args[0]);
-        new DatamartController().run(datalake);
-
-    }
-
-}

### 2023-11-05 InverseIndex/DatamartTest/src/main/java/org/example/MetadataExtractor.java

@@ -1,70 +1,0 @@
-package org.example;
-
-import com.fasterxml.jackson.databind.JsonNode;
-import com.fasterxml.jackson.databind.ObjectMapper;
-import dbManager.CreateTable;
-import objects.Book;
-
-import java.io.File;
-import java.util.Objects;
-
-public class MetadataExtractor {
-
-    public void filter(File datalake) {
-        File[] books = datalake.listFiles();
-
-
-        try {
-            if (books != null) {
-                for (File book : books) {
-                    String fileName = book.getName();
-                    System.out.println(fileName);
-
-                    if (fileName.endsWith(".json")) {
-                        int docId = Integer.parseInt(fileName.substring(0, fileName.length() - 5));
-                        ObjectMapper objectMapper = new ObjectMapper();
-                        JsonNode rootNode = objectMapper.readTree(book);
-
-                        String date = null;
-                        String author = null;
-                        String text = null;
-                        String title = null;
-                        String lang = null;
-
-                        if (rootNode.has("date")) {
-                            date = rootNode.get("date").asText();
-                        }
-
-                        if (rootNode.has("author")) {
-                            author = rootNode.get("author").asText();
-                        }
-
-                        if (rootNode.has("text")) {
-                            text = rootNode.get("text").asText();
-                        }
-
-                        if (rootNode.has("title")) {
-                            title = rootNode.get("title").asText();
-                        }
-
-                        if (rootNode.has("lang")) {
-                            lang = rootNode.get("lang").asText();
-                        }
-
-
-                        Book content = new Book(docId, date, author, text, title, lang);
-
-                        new CreateTable().insertBookTable(Objects.requireNonNull(content));
-
-                    }
-                }
-                System.out.println("File finished\n");
-            }
-
-        } catch (Exception e) {
-            System.out.println("Error: " + e.getMessage());
-        }
-
-    }
-
-}

### 2023-11-05 InverseIndex/DatamartTest/src/main/java/org/example/WordsExtractor.java

@@ -1,9 +1,0 @@
-package org.example;
-
-import dbManager.CreateTable;
-
-public class WordsExtractor {
-    public void filter(){
-        new CreateTable().insertWordsTable("hola", "adios");
-    }
-}

### 2023-11-05 InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/Indexer.java

@@ -10,7 +10,7 @@ import java.util.function.Predicate;
 
 public class Indexer {
 	private static final int MAX_TOKEN_LENGTH = 20;
-	private static final Set<Character> PUNCTUATION_SET = Set.of('.', ',', ';', ':', '?', '!', '¡', '¿', '(', ')', '*', '"');
+	private static final Set<Character> PUNCTUATION_SET = Set.of('.', ',', ';', ':', '?', '!', '¡', '¿', '(', ')', '*', '"', '[', ']', '“', '$', '’', '/', '\\');
 	private static final Set<Character> TOKEN_INNER_CHAR_SET = Set.of('\'', '-', '_');
 
 	private final FileDatalake datalake;
@@ -96,13 +96,18 @@ public class Indexer {
 		Set<Integer> indexedDocuments = datamart.documents();
 		Set<Integer> datalakeDocuments = datalake.documents();
 		datalakeDocuments.removeAll(indexedDocuments);
+		System.out.println("Indexing " + datalakeDocuments.size() + " documents");
 		for (Integer document: datalakeDocuments) {
+			System.out.println("Indexing document " + document);
 			Set<String> tokens = tokenizeDocument(document);
+			System.out.println("Document " + document + " has " + tokens.size() + " tokens");
 			datamart.add(document, tokens);
+			System.out.println("Document " + document + " indexed");
 		}
 
 		datalake.blockAndListen((document, content) -> {
 			try {
+				System.out.println("Indexing document " + document);
 				Set<String> tokens = tokenize(content);
 				datamart.add(document, tokens);
 			} catch (Exception e) {

### 2023-11-05 InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/Main.java

@@ -2,6 +2,7 @@ package es.ulpgc.bigdata.inverse_index.indexer;
 
 import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
 import es.ulpgc.bigdata.inverse_index.datamart.file.FileDatamart;
+import es.ulpgc.bigdata.inverse_index.datamart.sql.SqlDatamart;
 
 import java.nio.file.Path;
 
@@ -10,10 +11,7 @@ public class Main {
 		//assert that the arguments are correct
 		if (args.length != 2) {
 			System.out.println("Usage: java -jar indexer.jar <datalake> <datamart>");
-			System.out.println("Num args: " + args.length);
-			for(String arg: args) {
-				System.out.println(arg);
-			}
+
 			System.exit(1);
 		}
 		FileDatalake datalake = new FileDatalake(Path.of(args[0]));

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/ContentExtractor.java

@@ -1,46 +1,0 @@
-package es.ulpgc.bigdata;
-
-import java.io.BufferedReader;
-import java.io.IOException;
-import java.io.InputStreamReader;
-import java.net.HttpURLConnection;
-import java.net.URL;
-
-
-public class ContentExtractor {
-
-    public static String textExtractor(int id) {
-        String url = "https://www.gutenberg.org/cache/epub/" + id + "/pg" + id + ".txt";
-
-        try {
-            URL obj = new URL(url);
-            HttpURLConnection con = (HttpURLConnection) obj.openConnection();
-
-            //HTTP request
-            con.setRequestMethod("GET");
-
-            int responseCode = con.getResponseCode();
-            if (responseCode == HttpURLConnection.HTTP_OK) {
-                BufferedReader in = new BufferedReader(new InputStreamReader(con.getInputStream()));
-                String inputLine;
-                StringBuilder response = new StringBuilder();
-
-                while ((inputLine = in.readLine()) != null) {
-                    response.append(inputLine);
-                    response.append("\n"); //add line breaks to maintain the text format
-                }
-                in.close();
-                return response.toString();
-            }
-            else {
-                System.out.println("An error occurred while retrieving the text from the book " + id + ", response code: " + responseCode);
-                return null;
-            }
-        }
-        catch (IOException e) {
-            System.out.println("Error when trying to obtain the text from the book " + id);
-            e.printStackTrace();
-            return null;
-        }
-    }
-}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/Controller.java

@@ -1,60 +1,0 @@
-package es.ulpgc.bigdata;
-
-import java.io.File;
-import java.util.Timer;
-import java.util.TimerTask;
-
-import static spark.Spark.init;
-import static spark.Spark.port;
-
-public class Controller {
-    private TimerTask task;
-    private File datalakeRoot;
-
-    public Controller(File datalakeRoot) {
-        this.datalakeRoot = datalakeRoot;
-    }
-
-    public void start() {
-        Timer timer = new Timer();
-        task = new TimerTask() {
-            public void run() {
-                executeProgram();
-            }
-        };
-        timer.scheduleAtFixedRate(task, 0, TimerAPI.getTimerPeriod());
-    }
-
-    private void executeProgram() {
-        ContentExtractor contentExtractor = new ContentExtractor();
-        FileSystemDatalake dataLake = new FileSystemDatalake(datalakeRoot);
-
-        int id = 1;
-        int millisecondsPerMinute = 60_000;
-
-        while (id <= TimerAPI.getMaxBooks()) {
-            long startTime = System.currentTimeMillis();
-            int booksDownloadedThisMinute = 0;
-
-
-            while (booksDownloadedThisMinute < TimerAPI.getBooksPerMinute()) {
-                String bookText = ContentExtractor.textExtractor(id);
-
-                if (bookText != null) {
-                    FileSystemDatalake.saveText(id, bookText);
-                    booksDownloadedThisMinute++;
-                }
-                id++;
-            }
-
-            long elapsedTime = System.currentTimeMillis() - startTime;
-            if (elapsedTime < millisecondsPerMinute) {
-                try {
-                    Thread.sleep(millisecondsPerMinute - elapsedTime);
-                } catch (InterruptedException e) {
-                    e.printStackTrace();
-                }
-            }
-        }
-    }
-}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/Document.java

@@ -1,17 +1,0 @@
-package es.ulpgc.bigdata;
-
-public class Document {
-    private final String title;
-    private final String author;
-    private final String date;
-    private final String lang;
-    private final String text;
-
-    public Document(String title, String author, String date, String lang, String text) {
-        this.title = title;
-        this.author = author;
-        this.date = date;
-        this.lang = lang;
-        this.text = text;
-    }
-}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/FileSystemDatalake.java

@@ -1,60 +1,0 @@
-package es.ulpgc.bigdata;
-
-import com.google.gson.Gson;
-import com.google.gson.GsonBuilder;
-
-import java.io.*;
-import java.util.Map;
-import java.util.Scanner;
-
-public class FileSystemDatalake {
-    private static File datalakeRoot;
-
-    public FileSystemDatalake(File datalakeRoot) {
-        FileSystemDatalake.datalakeRoot = datalakeRoot;
-        //check if the root directory of the Datalake already exists
-        if (!datalakeRoot.exists()) {
-            //attempt to create the root directory
-            if (FileSystemDatalake.datalakeRoot.mkdirs()) {
-                System.out.println("The Datalake has been successfully created at: " + datalakeRoot.getAbsolutePath());
-            } else {
-                System.out.println("The Datalake could not be created at: " + datalakeRoot.getAbsolutePath());
-            }
-        } else {
-            System.out.println("The Datalake already exists in: " + datalakeRoot.getAbsolutePath());
-        }
-    }
-
-    public static void saveText(int id, String text) {
-        File file = new File(datalakeRoot, id + ".json");
-        try {
-            Map<String, String> dat = LibroGutenberg.transform(id, text);
-            if (dat != null) {
-                File jsonFile = new File(datalakeRoot, id + ".json");
-                if (file.exists()){
-                    try (FileWriter writer = new FileWriter(jsonFile)) {
-                        //converts the data to JSON and write in the file
-                        Gson gson = new GsonBuilder().setPrettyPrinting().create();
-                        String json = gson.toJson(dat);
-                        writer.write(json);
-                        System.out.println("File '"+ id +".json"+"' has been succesfully updated");
-                    }
-                } else{
-                    try (FileWriter writer = new FileWriter(jsonFile)) {
-                        //converts the data to JSON and write in the file
-                        Gson gson = new GsonBuilder().setPrettyPrinting().create();
-                        String json = gson.toJson(dat);
-                        writer.write(json);
-                        System.out.println("Saved '" + id + ".json'");
-                    }
-                }
-
-            } else {
-                System.out.println("It couldn't be saved because the content of the book " + id + " is empty");
-            }
-        } catch (IOException e) {
-            System.out.println("Error while saving " + id + ", with this exception: " + e);
-            e.printStackTrace();
-        }
-    }
-}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/LibroGutenberg.java

@@ -1,54 +1,0 @@
-package es.ulpgc.bigdata;
-import java.util.*;
-import java.util.regex.Matcher;
-import java.util.regex.Pattern;
-
-
-public class LibroGutenberg {
-
-    public static Map<String, String> transform(int id, String text) {
-        //this is a list of tuples where each tuple contains the attribute name and an associated regular expression for searching that attribute in the text
-        List<AbstractMap.SimpleEntry<String, Pattern>> attributes = Arrays.asList(
-                new AbstractMap.SimpleEntry<>("title", Pattern.compile("Title: (.*)", Pattern.CASE_INSENSITIVE)),
-                new AbstractMap.SimpleEntry<>("author", Pattern.compile("(?:Author|Creator|Contributor): (.*)", Pattern.CASE_INSENSITIVE)),
-                new AbstractMap.SimpleEntry<>("date", Pattern.compile("Release date: (.*)", Pattern.CASE_INSENSITIVE)),
-                new AbstractMap.SimpleEntry<>("lang", Pattern.compile("Language: (.*)", Pattern.CASE_INSENSITIVE))
-        );
-
-        //these are regular expressions that search for the start and end marks of the book within the text.
-        //these marks have the format "*** START OF ... " and "END OF ... ***," are used to delimit the main content of the book.
-        Pattern startPattern = Pattern.compile("(\\*\\*\\* START OF (THE|THIS) PROJECT GUTENBERG EBOOK.*?\\*\\*\\*)");
-        Pattern endPattern = Pattern.compile("(\\*\\*\\* END OF (THE|THIS) PROJECT GUTENBERG EBOOK.*?\\*\\*\\*)");
-
-        Map<String, String> data = new HashMap<>();
-
-        try {
-            for (AbstractMap.SimpleEntry<String, Pattern> attribute : attributes) {
-                Matcher matcher = attribute.getValue().matcher(text);
-                if (matcher.find()) {
-                    data.put(attribute.getKey(), matcher.group(1));
-                } else {
-                    System.out.println("Couldn't parse " + attribute.getKey() + " for " + id);
-                }
-            }
-
-            Matcher startMatcher = startPattern.matcher(text);
-            Matcher endMatcher = endPattern.matcher(text);
-
-            if (startMatcher.find() && endMatcher.find()) {
-                String bookText = text.substring(startMatcher.end(), endMatcher.start());
-                data.put("text", bookText);
-            } else {
-                System.out.println("Error parsing text for " + id);
[…]

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/Main.java

@@ -1,24 +1,0 @@
-package es.ulpgc.bigdata;
-
-import java.io.File;
-
-
-import java.io.File;
-
-import static java.lang.Thread.sleep;
-import static spark.Spark.init;
-import static spark.Spark.port;
-
-public class Main {
-    public static void main(String[] args) throws InterruptedException {
-        port(4567);
-        TimerAPI.setupTimerAPI();
-        init();
-
-        File datalakeRoot = new File(args[0]);
-        Controller controller = new Controller(datalakeRoot);
-        controller.start();
-
-    }
-}
-

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/TimerAPI.java

@@ -1,61 +1,0 @@
-package es.ulpgc.bigdata;
-
-import static spark.Spark.*;
-
-public class TimerAPI {
-    private static long timerPeriod = 5 * 60_000; // 5 minutes in milliseconds by default
-    private static int booksPerMinute = 100; // 100 books per minute by default
-    private static int maxBooks = 1000; // 1000 max books by default
-
-    public static void setupTimerAPI() {
-        post("/v1/execution/configuration", (request, response) -> {
-            System.out.println("\n");
-            if (request.queryParams().contains("maxbooks")) {
-                int max = Integer.parseInt(request.queryParams("maxbooks"));
-                setMaxBooks(max);
-                System.out.println("Max books successfully setted on: " + getMaxBooks());
-            }
-            if (request.queryParams().contains("booksperminute")) {
-                int books = Integer.parseInt(request.queryParams("booksperminute"));
-                setBooksPerMinute(books);
-                System.out.println("Books per minute successfully settled on: " + getBooksPerMinute());
-
-            }
-            if (request.queryParams().contains("timerperiod")) {
-                long minutes = Long.parseLong(request.queryParams("timerperiod"));
-                setTimerPeriod(minutes);
-                System.out.println("Timer period successfully settled on: " + getTimerPeriod()/60_000 + " minutes");
-
-            }
-            System.out.println("\n");
-            response.status(200);
-            response.body("Execution configuration set successfully. Max books: " + getMaxBooks() + ", Books per minute: " + getBooksPerMinute() + " and Timer period set on: " + getTimerPeriod() / 60_000 + " minutes.");
-            return null;
-        });
-
-    }
-
-    public static void setTimerPeriod(long minutes) {
-        timerPeriod = minutes * 60_000;
-    }
-
-    public static void setBooksPerMinute(int books) {
-        booksPerMinute = books;
-    }
-
-    public static void setMaxBooks(int max) {
-        maxBooks = max;
-    }
-
-    public static long getTimerPeriod() {
-        return timerPeriod;
-    }
-
-    public static int getBooksPerMinute() {
-        return booksPerMinute;
-    }
-
-    public static int getMaxBooks() {
-        return maxBooks;
-    }
-}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Datamart/src/main/java/es/ulpgc/bigdata/inverse_index/datamart/Datamart.java

@@ -1,9 +1,0 @@
-package es.ulpgc.bigdata.inverse_index.datamart;
-
-import java.util.Set;
-
-public interface Datamart {
-	Set<Integer> index(String token) throws Exception;
-	Set<Integer> documents() throws Exception;
-	void add(int document, Set<String> tokens) throws Exception;
-}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Datamart/src/main/java/es/ulpgc/bigdata/inverse_index/datamart/file/FileDatamart.java

@@ -1,104 +1,0 @@
-package es.ulpgc.bigdata.inverse_index.datamart.file;
-
-import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
-
-import java.io.IOException;
-import java.nio.file.Files;
-import java.nio.file.Path;
-import java.util.HashSet;
-import java.util.Set;
-
-public class FileDatamart implements Datamart {
-	private final Path root;
-
-	public FileDatamart(Path root) throws IOException {
-		this.root = root;
-
-		if (Files.exists(root)) {
-			// The root already exists, assert that it's a directory and follows the format specified
-			if (!Files.isDirectory(root)) {
-				throw new IllegalArgumentException("The root must be a directory");
-			}
-		} else {
-			// The root doesn't exist, create it
-			Files.createDirectories(root);
-		}
-	}
-
-	private Path assertWord (String word) throws Exception {
-		//TODO: handle edge cases
-		String beginning = word.substring(0, 2);
-		Path neighbourDir = root.resolve(beginning);
-		if (!Files.isDirectory(neighbourDir)) {
-			if (Files.exists(neighbourDir)) {
-				throw new Exception("Unexpected file in datamart " + neighbourDir);
-			}
-			Files.createDirectory(neighbourDir);
-		}
-		Path wordFile = neighbourDir.resolve(word);
-		if (!Files.isRegularFile(wordFile)) {
-			if (Files.exists(wordFile)) {
-				throw new Exception("Unexpected non file in datamart " + wordFile);
-			}
-			Files.createFile(wordFile);
-		}
-
-		return wordFile;
-	}
-
-	private Set<Integer> readWordFile(Path wordFile) throws IOException {
-		byte[] content = Files.readAllBytes(wordFile);
-		Set<Integer> documents = new HashSet<>();
-		for (int i = 0; i < content.length; i += 4) {
-			documents.add(byteToInt(content, i));
-		}
-		return documents;
-	}
-
-	private int byteToInt(byte[] bytes, int offset) {
-		return (bytes[offset] << 24) | (bytes[offset + 1] << 16) | (bytes[offset + 2] << 8) | bytes[offset + 3];
-	}
-
-	@Override
-	public Set<Integer> index(String token) throws Exception {
-		Path wordFile = assertWord(token);
-		return readWordFile(wordFile);
-	}
-
-	@Override
-	public Set<Integer> documents() throws IOException {
[…]

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Datamart/src/main/java/es/ulpgc/bigdata/inverse_index/datamart/sql/SqlDatamart.java

@@ -1,61 +1,0 @@
-package es.ulpgc.bigdata.inverse_index.datamart.sql;
-
-import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
-
-import java.nio.file.Path;
-import java.sql.*;
-import java.util.HashSet;
-import java.util.Set;
-
-public class SqlDatamart implements Datamart {
-	private final Connection conn;
-
-	public SqlDatamart(Path path) throws SQLException {
-		String url =  "jdbc:sqlite:" + path;
-		this.conn = DriverManager.getConnection(url);
-		assertTables();
-	}
-
-	private void assertTables() throws SQLException {
-		// create table
-		Statement stmt = conn.createStatement();
-		stmt.execute("CREATE TABLE IF NOT EXISTS words (" +
-			"word TEXT, " +
-			"book INTEGER" +
-			")"
-		);
-	}
-
-	@Override
-	public Set<Integer> index(String token) throws Exception {
-		Set<Integer> documents = new HashSet<>();
-		PreparedStatement stmt = conn.prepareStatement("SELECT DISTINCT  book FROM words WHERE word = ?");
-		stmt.setString(1, token);
-		ResultSet results = stmt.executeQuery();
-		while (results.next()) {
-			documents.add(results.getInt(1));
-		}
-		return documents;
-	}
-
-	@Override
-	public Set<Integer> documents() throws Exception {
-		Set<Integer> documents = new HashSet<>();
-		Statement stmt = conn.createStatement();
-		ResultSet results = stmt.executeQuery("SELECT DISTINCT book FROM words");
-		while(results.next()) {
-			documents.add(results.getInt(1));
-		}
-		return documents;
-	}
-
-	@Override
-	public void add(int document, Set<String> tokens) throws Exception {
-		PreparedStatement stmt = conn.prepareStatement("INSERT INTO words (word, book) VALUES (?, ?)");
-		for (String token : tokens) {
-			stmt.setString(1, token);
-			stmt.setInt(2, document);
-			stmt.executeUpdate();
-		}
-	}
-}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/FileDatalake.java

@@ -1,60 +1,0 @@
-package es.ulpgc.bigdata.inverse_index.indexer;
-
-import com.google.gson.Gson;
-import com.google.gson.JsonObject;
-
-import java.io.IOException;
-import java.nio.file.Files;
-import java.nio.file.Path;
-import java.nio.file.WatchKey;
-import java.nio.file.WatchService;
-import java.util.HashSet;
-import java.util.Set;
-import java.util.function.BiConsumer;
-import java.util.function.Predicate;
-import java.util.regex.Pattern;
-
-public class FileDatalake {
-	private final Path root;
-
-	public FileDatalake(Path root) {
-		this.root = root;
-	}
-
-
-	public Set<Integer> documents() throws IOException {
-		Set<Integer> documents = new HashSet<>();
-		Predicate<String> isDocument = Pattern.compile("\\d+\\.json").asMatchPredicate();
-		for (Path document: Files.list(root).toList()) {
-			if (!Files.isRegularFile(document)) continue;
-			String name = document.getFileName().toString();
-			if (!isDocument.test(name)) continue;
-			documents.add(Integer.parseInt(name.split("\\.")[0]));
-		}
-		return documents;
-	}
-
-	public String readDocument(int document) throws IOException {
-		Gson gson = new Gson();
-		JsonObject el = gson.fromJson(Files.readString(root.resolve(document + ".json")), JsonObject.class);
-		return el.get("text").getAsString();
-	}
-
-	public void blockAndListen(BiConsumer<Integer, String> documentConsumer) throws IOException, InterruptedException {
-		WatchService ws = root.getFileSystem().newWatchService();
-		root.register(ws, java.nio.file.StandardWatchEventKinds.ENTRY_MODIFY);
-		for (;;) {
-			WatchKey key = ws.take();
-			for (var event : key.pollEvents()) {
-				String name = event.context().toString();
-				if (!Pattern.compile("\\d+\\.json").asMatchPredicate().test(name)) continue;
-				int document = Integer.parseInt(name.split("\\.")[0]);
-				documentConsumer.accept(document, readDocument(document));
-			}
-			boolean valid = key.reset();
-			if (!valid) {
-				break;
-			}
-		}
-	}
-}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/Indexer.java

@@ -1,113 +1,0 @@
-package es.ulpgc.bigdata.inverse_index.indexer;
-
-import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
-
-import java.io.IOException;
-import java.util.HashSet;
-import java.util.Set;
-import java.util.function.BiConsumer;
-import java.util.function.Predicate;
-
-public class Indexer {
-	private static final int MAX_TOKEN_LENGTH = 20;
-	private static final Set<Character> PUNCTUATION_SET = Set.of('.', ',', ';', ':', '?', '!', '¡', '¿', '(', ')', '*', '"');
-	private static final Set<Character> TOKEN_INNER_CHAR_SET = Set.of('\'', '-', '_');
-
-	private final FileDatalake datalake;
-	private final Datamart datamart;
-
-	public Indexer(FileDatalake datalake, Datamart datamart) {
-		this.datalake = datalake;
-		this.datamart = datamart;
-	}
-
-	public static Set<String> tokenize(String document) {
-		Set<String> tokens = new HashSet<>();
-		int currTokenStart = 0;
-		int safeTokenEnd = 0;
-		IndexerState state = IndexerState.OutOfToken;
-
-		Predicate<Character> isWhitespaceOrPunctuation = c -> Character.isWhitespace(c) || PUNCTUATION_SET.contains(c);
-		Predicate<Character> isTokenCharacter = c -> Character.isLetter(c) || Character.isDigit(c);
-
-		BiConsumer<Integer, Integer> addToken = (start, end) -> tokens.add(document.substring(start, end).toLowerCase());
-
-		for (int i = 0; i < document.length(); i++) {
-			char c = document.charAt(i);
-			int tokenLength = i - currTokenStart;
-			switch (state) {
-				case OutOfToken:
-					if (isTokenCharacter.test(c)) {
-						state = IndexerState.InToken;
-					} else if (isWhitespaceOrPunctuation.test(c) || TOKEN_INNER_CHAR_SET.contains(c)) {
-						currTokenStart = i + 1;
-					}
-					break;
-				case InToken:
-					// the last character was valid for a token, so the current index would be a safe end.
-					safeTokenEnd = i;
-					if (tokenLength > MAX_TOKEN_LENGTH) {
-						state = IndexerState.InInvalidToken;
-					}
-					if (isWhitespaceOrPunctuation.test(c)) {
-						state = IndexerState.OutOfToken;
-						addToken.accept(currTokenStart, safeTokenEnd);
[…]

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/IndexerState.java

@@ -1,12 +1,0 @@
-package es.ulpgc.bigdata.inverse_index.indexer;
-
-public enum IndexerState {
-	// it is a regular token, but it is not finished yet, add it to the current token when it is finished
-	InToken,
-	// the current token is valid, but it has some trailing characters that aren't valid if they're the last ones
-	InValidTokenUnknownEnd,
-	// Even though we are in a token, it is not valid and thus we should ignore it and go to the next one
-	InInvalidToken,
-	OutOfToken,
-
-}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/Main.java

@@ -1,24 +1,0 @@
-package es.ulpgc.bigdata.inverse_index.indexer;
-
-import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
-import es.ulpgc.bigdata.inverse_index.datamart.file.FileDatamart;
-
-import java.nio.file.Path;
-
-public class Main {
-	public static void main(String[] args) throws Exception {
-		//assert that the arguments are correct
-		if (args.length != 2) {
-			System.out.println("Usage: java -jar indexer.jar <datalake> <datamart>");
-			System.out.println("Num args: " + args.length);
-			for(String arg: args) {
-				System.out.println(arg);
-			}
-			System.exit(1);
-		}
-		FileDatalake datalake = new FileDatalake(Path.of(args[0]));
-		Datamart datamart = new FileDatamart(Path.of(args[1]));
-		Indexer indexer = new Indexer(datalake, datamart);
-		indexer.index();
-	}
-}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/Indexer/src/test/java/es/ulpgc/bigdata/inverse_index/IndexerTest.java

@@ -1,52 +1,0 @@
-package es.ulpgc.bigdata.inverse_index;
-
-import es.ulpgc.bigdata.inverse_index.indexer.Indexer;
-import org.junit.jupiter.api.Test;
-
-import java.util.Set;
-
-import static org.junit.jupiter.api.Assertions.*;
-
-class IndexerTest {
-		@Test
-		void indexbasic() {
-			String text = "This is a test!";
-			Set<String> tokens = Indexer.tokenize(text);
-			assertEquals(Set.of("this", "is", "a", "test"), tokens);
-		}
-
-		@Test
-		void indexDash() {
-			String text = "This is a test-test!";
-			Set<String> tokens = Indexer.tokenize(text);
-			assertEquals(Set.of("this", "is", "a", "test-test"), tokens);
-		}
-
-		@Test
-		void indexUnderscorePrefixPostfix() {
-			String text = "This is a test_ _test";
-			Set<String> tokens = Indexer.tokenize(text);
-			assertEquals(Set.of("this", "is", "a", "test"), tokens);
-		}
-
-		@Test
-	void indexLotsOfWhitespace() {
-		String text = "This is a test!   \n\n\nnew line!";
-		Set<String> tokens = Indexer.tokenize(text);
-		assertEquals(Set.of("this", "is", "a", "test", "new", "line"), tokens);
-		}
-
-		@Test
-		void indexNumbers() {
-			String text = "1234 7777 23";
-			Set<String> tokens = Indexer.tokenize(text);
-			assertEquals(Set.of("1234", "7777", "23"), tokens);
-		}
-
-		@Test
-		void indexTooLongToken() {
-			String text = "short _long123456789123456789_ after other________________________________long";
-			Set<String> tokens = Indexer.tokenize(text);
-			assertEquals(Set.of("short", "after"), tokens);
-		}
-}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/Main.java

@@ -1,7 +1,0 @@
-package es.ulpgc.bigdata.inverse_index;
-
-public class Main {
-	public static void main(String[] args) {
-		new Controller().startServers();
-	}
-}

### 2023-11-05 inverse-index-big-data-main/InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/SparkWebService.java

@@ -1,42 +1,0 @@
-package es.ulpgc.bigdata.inverse_index;
-
-
-
-
-import com.google.gson.Gson;
-import spark.Spark;
-
-import java.util.List;
-
-public class SparkWebService {
-
-    public void startServer() {
-        Spark.port(4567);
-
-        Spark.get("/v1/search", (request, response) -> {
-            String word = request.queryParams("word");
-
-            if (word != null) {
-                try {
-                    SqliteReader sqliteReader = new SqliteReader();
-                    List<String> books = sqliteReader.getBooksForWord(word);
-
-                    if (!books.isEmpty()) {
-                        Gson gson = new Gson();
-                        response.type("application/json");
-                        return gson.toJson(books);
-                    } else {
-                        response.status(404); // Not Found
-                        return "Documents not found for the specified word.";
-                    }
-                } catch (Exception e) {
-                    response.status(400); // Bad Request
-                    return "Error processing the request: " + e.getMessage();
-                }
-            } else {
-                response.status(400); // Bad Request
-                return "You must provide either 'id' or 'word' as a query parameter.";
-            }
-        });
-    }
-}

### 2023-11-05 inverse-index-big-data-main/indexer/indexer_commons.py

@@ -1,55 +1,0 @@
-import json
-import os
-import sqlite3
-from tqdm import tqdm
-
-def document_generator(datalake):
-	books = os.listdir(datalake)
-	for book in tqdm(books):
-		# Combinamos la ruta completa con el nombre del archivo
-		archivo = os.path.join(datalake, book)
-
-		# Verificamos si el archivo es un archivo JSON
-		if book.endswith('.json'):
-			doc_id = int(book[:-5])
-			with open(archivo, 'r', encoding='utf-8') as archivo_json:
-				yield doc_id, json.load(archivo_json)
-
-def create_datamart(datalake_dir, datamart_path, index):
-	conn = sqlite3.connect(datamart_path)
-	c = conn.cursor()
-
-	# Crear la tabla "words" con dos columnas: palabra y lista de libros
-	c.execute("""
-		CREATE TABLE IF NOT EXISTS inv_index (
-		word TEXT,
-		doc_id INTEGER
-	)""")
-
-	c.execute("""
-		CREATE TABLE IF NOT EXISTS documents (
-		id INTEGER,
-		title TEXT,
-		date TEXT,
-		content TEXT
-	)""")
-
-	for word, docs in index.items():
-		for doc in docs:
-			c.execute("""
-					INSERT OR REPLACE INTO inv_index (word, doc_id) VALUES (?, ?)
-				""",
-				(word, doc)
-			)
-
-	for doc_id, doc in document_generator(datalake_dir):
-		c.execute(
-			"""INSERT OR REPLACE INTO documents (id, title, date, content)
-			VALUES (?, ?, ?, ?)
-			""",
-			(doc_id, doc.get("title"), doc.get("date"), doc.get("text"))
-		)
-
-	conn.commit()
-	conn.close()
-

### 2023-11-05 inverse-index-big-data-main/indexer/nltk_indexer.py

@@ -1,36 +1,0 @@
-import sys
-import nltk
-from collections import defaultdict
-from indexer_commons import document_generator, create_datamart
-
-def indexer(document_list):
-	"""
-	Creates an inverted word index based on a list of documents.
-	Args:
-		document_list (generator): A generator of tuples (doc_id, document), where
-			doc_id is the document identifier, and document is a dictionary containing
-			a 'text' key with the document's text.
-	Returns:
-		defaultdict: The inverted word index where keys are words, and values are sets
-		of document identifiers containing that word.
-	"""
-	index = defaultdict(set)
-	for doc_id, document in document_list:
-		text = document["text"]
-		# Tokenize the text into words using NLTK
-		words = set(nltk.word_tokenize(text))
-		for word in words:
-			index[word].add(doc_id)
-	return index
-
-if __name__ == "__main__":
-	if len(sys.argv) < 3:
-		print("Usage: python nltk_indexer.py <datalake> <datamart>")
-		exit(1)
-	# Ścieżka do katalogu z plikami JSON
-	datalake_path = sys.argv[1]
-
-	index = indexer(document_generator(datalake_path))
-
-	datamart_path = sys.argv[2]
-	create_datamart(datalake_path, datamart_path, index)

### 2023-11-05 inverse-index-big-data-main/indexer/spacy_indexer.py

@@ -1,42 +1,0 @@
-##Se instala el spacy y el en_core_web_sm
-import json
-import os
-import sys
-import spacy  
-from tqdm import tqdm
-from collections import defaultdict
-
-from indexer_commons import document_generator, create_datamart
-
-def indexer(documents):
-	reverse_index = defaultdict(set)
-	for doc_id, document in documents:
-		texto = document.get("text")
-		texto_sobrante = texto
-
-		while len(texto_sobrante) > 0:
-			if len(texto_sobrante) > 1_000_000:
-				candidato = texto_sobrante[:1_000_000]
-				index = candidato.rfind(" ")
-				texto_seccion = texto_sobrante[:index]
-				texto_sobrante = texto_sobrante[index:]
-			else:
-				texto_seccion, texto_sobrante = texto_sobrante, ""
-
-			nlp = spacy.load("en_core_web_sm")
-			doc = nlp(texto_seccion) # Crea un objeto de spacy tipo nlp
-			lexical_tokens = [t.orth_ for t in doc if not (t.is_punct or t.is_stop)]
-			unique_tokens = set(lexical_tokens)
-
-			for word in unique_tokens:
-				reverse_index[word].add(doc_id)
-	return reverse_index
-
-if __name__ == "__main__":
-	if len(sys.argv) < 3:
-		print("Usage: python spacy_index.py <datalake> <datamart>")
-		exit(1)
-	datalake_dir = sys.argv[1]
-	index = indexer(document_generator(datalake_dir))
-	datamart_path = sys.argv[2]
-	create_datamart(datalake_dir, datamart_path, index)

### 2023-11-05 inverse-index-big-data-main/scraper/scraper.py

@@ -1,74 +1,0 @@
-import sys
-import os
-import json
-import re
-import asyncio
-import aiohttp
-
-if len(sys.argv) < 2:
-	print("Usage: python3 scraper.py <datalake>")
-	exit(1)
-
-datalake_dir = sys.argv[1]
-
-os.makedirs(datalake_dir, exist_ok=True)
-
-def transform(id, text: str) -> str:
-	attributes = [
-		("title", re.compile(r"Title: (.*)", flags=re.IGNORECASE)),
-		("author", re.compile(r"(?:Author|Creator|Contributor): (.*)", flags=re.IGNORECASE)),
-		("date", re.compile(r"Release date: (.*)", flags=re.IGNORECASE)),
-		("lang", re.compile(r"Language: (.*)", flags=re.IGNORECASE))
-	]
-	start_re = re.compile(r"(\*\*\* START OF (THE|THIS) PROJECT GUTENBERG EBOOK.*?\*\*\*)")
-	end_re = re.compile(r"(\*\*\* END OF (THE|THIS) PROJECT GUTENBERG EBOOK.*?\*\*\*)")
-	data = {}
-	try:
-		for attr_name, attr_re in attributes:
-			m = attr_re.search(text)
-			if m:
-				data[attr_name] = m.group(1)
-			else :
-				print(f"Couldn't parse {attr_name} for {id}")
-		start_m = start_re.search(text)
-		end_m = end_re.search(text)
-		if not (start_m and end_m):
-			# this happens, for example, in doc 673
-			return None
-		data["text"] = text[start_m.end():end_m.start()]
-	except AttributeError as e:
-		print(f"Error parsing text for {id}")
-		print(e)
-		exit(1)
-	return data
-
-
-async def fetch(session, id):
-	async with session.get(f"https://www.gutenberg.org/cache/epub/{id}/pg{id}.txt") as response:
-		return (await response.text(), response.status)
-
-async def save_text(session, id):
-		text, status = await fetch(session, id)
-		if status != 200:
-			print(f"{id} could not be fetched")
-			return
-
-		text = text.replace("\r\n", "\n")
-		dat = transform(id, text)
-		if dat is None:
-			print(f"{id} is not a document")
-			return
-
-		with open(os.path.join(datalake_dir, f"{id}.json"), "w") as f:
-			json.dump(dat, f)
-		print(f"Saved {id}")
-
-async def main():
-	async with aiohttp.ClientSession() as session:
[…]

### 2023-11-05 latexJava/paperJava.tex
added datamart to paperJava.tex

@@
 
+\subsection{Datamart}
+
+The Datamart module handles the storage and management of the inverted index.
+It defines methods for indexing keywords, retrieving documents associated with a keyword, and obtaining a list of all available documents in the index.
+Two implementations are provided: a SQL-based Datamart using SQLite and a File-based Datamart using file storage.
+\begin{itemize}
+
+\item 
+The SQL-based Datamart in \texttt{SqlDatamart} module stores the inverted index using a SQL database, associating keywords with document lists.
+
+\item 
+The File-based Datamart in \texttt{FileDatamart} module employs file storage to maintain the inverted index, where each keyword corresponds to a file containing document IDs. 
+\end{itemize}
+The Datamart module provides a reliable solution for the storage and retrieval of the inverted index. The choice between provided implementations depends on project requirements and scale.
+File-Based approach is suitable for smaller-scale projects where a full database system might be unnecessary, offering flexibility and efficiency in data storage.
+
 \section{Results and conclusions}

### 2023-11-05 latexJava/paperJava.tex
Edit Indexer section in paper

@@
 \item
-The \texttt{IndexerState} enumeration defines various states that may occur during the tokenization of a document's text.
-States such as \textit{InToken}, \textit{InInvalidTokenUnknownEnd}, \textit{InInvalidToken}, and \textit{OutOfToken} describe different tokenization scenarios.
-
-\item
-The \texttt{Indexer} class is responsible for creating an inverted index based on documents stored in the \texttt{FileDatalake} and storing it in the \texttt{Datamart}.
+The \texttt{Indexer} class is responsible for creating an inverted index based on documents stored in the \texttt{FileDatalake} and storing it in the \texttt{Datamart}, with the actual implementation being injected as a dependency on creation.
 The class provides the following functionalities:
@@
 \begin{itemize}
-  \item \texttt{tokenize(String document)}: Tokenizes the text content of a document, splitting it into individual words (tokens), removing punctuation, and preparing tokens for indexing.
+  \item \texttt{tokenize(String document)}: Tokenizes the text content of a document, this is done using a state machine pattern that processes the text character by character, trying to be much more efficient than a regular expression.
+		It returns a set of tokens found in the document.
   \item \texttt{index()}: Initiates the indexing process. It creates an inverted index from the available documents in the \texttt{FileDatalake} and stores it in the \texttt{Datamart}.
+		After it finishes, it blocks in a loop, listening in on new documents being added to the datalake, and updating the index accordingly as they are added.
 \end{itemize}
@@
 \item 
-The \texttt{IndexerTest} class contains a set of unit tests for the \texttt{Indexer} class.
-These tests verify the correct behavior of the \texttt{tokenize} method in various scenarios (such as checking if it copes with underscores  at the beginning or at the end of words), ensuring the accuracy of tokenization.
+The \texttt{IndexerState} enumeration defines the states for the tokenization state machine used by the \texttt{Indexer} class. The states are as follows:
+
+\begin{itemize}
+	\item \texttt{OutOfToken} The state machine is not currently processing a token.
+	\item \texttt{InToken} The state machine is currently processing a token.
+	\item \texttt{InValidTokenUnknownEnd} The state machine is in an ambiguous position, where whenever the current token ends early or continues depends on future characters.
+	\item \texttt{InInvalidToken} The state machine is currently processing an invalid token, and thus should ignore future valid characters until the token ends.
+		This can for example occur when the token is too long, as no one is going to search for tokens that are many times longer than an average word.
+\end{itemize}
 \end{itemize}
@@
 It accepts two command-line arguments: the path to the \texttt{datalake} (data source) and \texttt{datamart} (destination for the inverted index).
-The program creates instances of \texttt{FileDatalake} and \texttt{Datamart} and then initiates the indexing process using the \texttt{Indexer} class.
+The program creates instances of \texttt{FileDatalake} and an instance the \texttt{Datamart} and then initiates the indexing process using the \texttt{Indexer} class.
+Aditionally, this module has various unit tests for ensuring the correctness and robustness of the tokenization implementation,
+as this part is the most complex and error-prone in the project, especially considering that it deals with any arbitrary unvetted text coming in from the internet.
 

### 2023-11-05 InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/Indexer.java
Improvements in the tokenization

@@ -10,7 +10,6 @@ import java.util.function.Predicate;
 
 public class Indexer {
 	private static final int MAX_TOKEN_LENGTH = 20;
-	private static final Set<Character> PUNCTUATION_SET = Set.of('.', ',', ';', ':', '?', '!', '¡', '¿', '(', ')', '*', '"', '[', ']', '“', '$', '’', '/', '\\');
 	private static final Set<Character> TOKEN_INNER_CHAR_SET = Set.of('\'', '-', '_');
 
 	private final FileDatalake datalake;
@@ -27,7 +26,6 @@ public class Indexer {
 		int safeTokenEnd = 0;
 		IndexerState state = IndexerState.OutOfToken;
 
-		Predicate<Character> isWhitespaceOrPunctuation = c -> Character.isWhitespace(c) || PUNCTUATION_SET.contains(c);
 		Predicate<Character> isTokenCharacter = c -> Character.isLetter(c) || Character.isDigit(c);
 
 		BiConsumer<Integer, Integer> addToken = (start, end) -> tokens.add(document.substring(start, end).toLowerCase());
@@ -38,9 +36,8 @@ public class Indexer {
 			switch (state) {
 				case OutOfToken:
 					if (isTokenCharacter.test(c)) {
+						currTokenStart = i;
 						state = IndexerState.InToken;
-					} else if (isWhitespaceOrPunctuation.test(c) || TOKEN_INNER_CHAR_SET.contains(c)) {
-						currTokenStart = i + 1;
 					}
 					break;
 				case InToken:
@@ -49,28 +46,29 @@ public class Indexer {
 					if (tokenLength > MAX_TOKEN_LENGTH) {
 						state = IndexerState.InInvalidToken;
 					}
-					if (isWhitespaceOrPunctuation.test(c)) {
+					if (TOKEN_INNER_CHAR_SET.contains(c)) {
+						state = IndexerState.InValidTokenUnknownEnd;
+					} else if (!isTokenCharacter.test(c)) {
 						state = IndexerState.OutOfToken;
 						addToken.accept(currTokenStart, safeTokenEnd);
 						currTokenStart = i+1;
-					}
-					if (TOKEN_INNER_CHAR_SET.contains(c)) {
-						state = IndexerState.InValidTokenUnknownEnd;
 					}
 					break;
 				case InValidTokenUnknownEnd:
-					if (isWhitespaceOrPunctuation.test(c)) {
[…]

### 2023-11-05 InverseIndex/Indexer/src/test/java/es/ulpgc/bigdata/inverse_index/IndexerTest.java

@@ -49,4 +49,11 @@ class IndexerTest {
 			Set<String> tokens = Indexer.tokenize(text);
 			assertEquals(Set.of("short", "after"), tokens);
 		}
+
+		@Test
+	void indexTags() {
+			String text = "<<hello>> <world>";
+			Set<String> tokens = Indexer.tokenize(text);
+			assertEquals(Set.of("hello", "world"), tokens);
+		}
 }

### 2023-11-05 InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/FileDatalake.java
Refactored indexer to be more robust listening

@@ -16,6 +16,7 @@ import java.util.regex.Pattern;
 
 public class FileDatalake {
 	private final Path root;
+	private WatchService ws = null;
 
 	public FileDatalake(Path root) {
 		this.root = root;
@@ -40,9 +41,12 @@ public class FileDatalake {
 		return el.get("text").getAsString();
 	}
 
-	public void blockAndListen(BiConsumer<Integer, String> documentConsumer) throws IOException, InterruptedException {
+	public void startListener() throws IOException {
 		WatchService ws = root.getFileSystem().newWatchService();
 		root.register(ws, java.nio.file.StandardWatchEventKinds.ENTRY_MODIFY);
+	}
+
+	public void blockAndListen(BiConsumer<Integer, String> documentConsumer) throws IOException, InterruptedException {
 		for (;;) {
 			WatchKey key = ws.take();
 			for (var event : key.pollEvents()) {

### 2023-11-05 InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/Indexer.java

@@ -93,6 +93,8 @@ public class Indexer {
 		// get already indexed documents
 		Set<Integer> indexedDocuments = datamart.documents();
 		Set<Integer> datalakeDocuments = datalake.documents();
+		// Start the listener to listen for new documents that may have been added while we were indexing
+		datalake.startListener();
 		datalakeDocuments.removeAll(indexedDocuments);
 		System.out.println("Indexing " + datalakeDocuments.size() + " documents");
 		for (Integer document: datalakeDocuments) {

### 2023-11-05 InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/DocumentParser.java
Renamed class to english

@@ -4,7 +4,7 @@ import java.util.regex.Matcher;
 import java.util.regex.Pattern;
 
 
-public class LibroGutenberg {
+public class DocumentParser {
 
     public static Map<String, String> transform(int id, String text) {
         //this is a list of tuples where each tuple contains the attribute name and an associated regular expression for searching that attribute in the text

### 2023-11-05 InverseIndex/Crawler/src/main/java/es/ulpgc/bigdata/FileSystemDatalake.java

@@ -5,7 +5,6 @@ import com.google.gson.GsonBuilder;
 
 import java.io.*;
 import java.util.Map;
-import java.util.Scanner;
 
 public class FileSystemDatalake {
     private static File datalakeRoot;
@@ -28,7 +27,7 @@ public class FileSystemDatalake {
     public static void saveText(int id, String text) {
         File file = new File(datalakeRoot, id + ".json");
         try {
-            Map<String, String> dat = LibroGutenberg.transform(id, text);
+            Map<String, String> dat = DocumentParser.transform(id, text);
             if (dat != null) {
                 File jsonFile = new File(datalakeRoot, id + ".json");
                 if (file.exists()){

### 2023-11-05 latexJava/paperJava.tex
Added sections to paper

@@
 
+The biggest improvement is the new tokenization algorithm, which is orders of magnitude faster than the old methods used in the project.
+Also given that it is implemented by hand, it is much more flexible and can be easily modified to suit the needs of the project.
+
 The code of this project can be found in the following repository: \url{https://github.com/Aurora2500/inverse-index-big-data}
@@
 
-There are various ways in which this project could be improved.
+In the future, the new file datamart could be improved further to be faster using all sorts of different caching techniques to reduce the number of IO operations.
 

### 2023-11-05 latexJava/paperJava.tex
Improve query engine

@@
 \item
-The \texttt{LibroGutenberg} class is pivotal in the process of extracting meaningful information from the downloaded book text.
+The \texttt{DocumentParser} class is pivotal in the process of extracting meaningful information from the downloaded book text.
 It utilizes regular expressions to search for and identify various attributes, such as the book's title, author, publication date, language, and, most importantly, the book's actual textual content.
@@
 \item
-The \texttt{Controller} class serves as the controller in the Query Engine module.
-It is responsible for initializing and running a server that handles client requests.
-The \texttt{Controller} class invokes the \texttt{startServer} method of the \texttt{SparkWebService} object.
-
+The \texttt{SparkWebService} class utilizes the Spark library to launch an HTTP server. This server listens on a specified port and handles HTTP requests. It provides two endpoints,
+\begin{itemize}
+	\item \texttt{/v1/search}, allowing users to search for documents based on keywords, with a pagination feature for retrieving results in batches.
+	\item \texttt{/v1/document/:id}, allowing users to get a particular document.
+\end{itemize}
 \item
-The \texttt{SparkWebService} class utilizes the Spark library to launch an HTTP server.
-This server listens on a specified port and handles HTTP requests, particularly GET requests.
-It provides a single main query, \texttt{/v1/search}, allowing users to search for documents based on keywords.
-
-\item
-The \texttt{SqliteReader} class is responsible for communication with the SQLite database, which stores information about keyword indexes within documents.
-When the server receives a request with a keyword, the \texttt{SqliteReader} extracts information about the documents containing that keyword from the database.
 
@@
 The \texttt{Main} class contains the \texttt{main} function, which serves as the entry point for the Query Engine module.
-It primarily initializes a \texttt{Controller} object and starts the API server.
-
-The collaboration among these classes is as follows: The Spark server listens for search requests and, upon receiving a query, forwards it to the \texttt{SqliteReader}.
-The \texttt{SqliteReader} communicates with the SQLite database to retrieve documents containing the specified keyword.
-The results are processed and returned to the client in JSON format via the Spark server.
-This allows users to search for documents based on keywords and receive results efficiently.
+It accepts two command-line arguments: the path to the \texttt{datalake}, which is where the documents themselves are stored, and to the datamart \texttt{datamart}, which is the index of all the documents.
+It then initializes the \texttt{SparkWebService} class and makes it listen for HTTP requests.
 
@@
 In the future, the new file datamart could be improved further to be faster using all sorts of different caching techniques to reduce the number of IO operations.
+Aditionally, various parts of the indexer could be improved further by having its own cache and flush features added, so that it doesn't flush all the indexed documents to the datamart one by one.
 

### 2023-11-05 InverseIndex/Datamart/src/main/java/es/ulpgc/bigdata/inverse_index/datamart/sql/SqlDatamart.java

@@ -6,9 +6,15 @@ import java.nio.file.Path;
 import java.sql.*;
 import java.util.HashSet;
 import java.util.Set;
+import java.util.concurrent.ScheduledExecutorService;
+import java.util.concurrent.ScheduledFuture;
+import java.util.concurrent.TimeUnit;
 
 public class SqlDatamart implements Datamart {
 	private final Connection conn;
+	private ScheduledFuture<?> debounceCommitFuture = null;
+	private final ScheduledExecutorService executorService = java.util.concurrent.Executors.newSingleThreadScheduledExecutor();
+	private final static int DEBOUNCE_TIME_MILLIS = 2000;
 
 	public SqlDatamart(Path path) throws SQLException {
 		String url =  "jdbc:sqlite:" + path;
@@ -52,6 +58,7 @@ public class SqlDatamart implements Datamart {
 
 	@Override
 	public void add(int document, Set<String> tokens) throws Exception {
+		debounceCommit();
 		PreparedStatement stmt = conn.prepareStatement("INSERT INTO words (word, book) VALUES (?, ?)");
 		for (String token : tokens) {
 			stmt.setString(1, token);
@@ -59,5 +66,19 @@ public class SqlDatamart implements Datamart {
 			stmt.executeUpdate();
 		}
 		stmt.close();
+	}
+
+	private void debounceCommit() {
+		if (debounceCommitFuture != null) {
+			debounceCommitFuture.cancel(false);
+		}
+
+		debounceCommitFuture = executorService.schedule(() -> {
+			try {
+				conn.commit();
+			} catch (SQLException e) {
+				e.printStackTrace();
+			}
+		}, DEBOUNCE_TIME_MILLIS, TimeUnit.MILLISECONDS);
 	}
 }

### 2023-11-05 InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/FileDatalake.java

@@ -42,7 +42,7 @@ public class FileDatalake {
 	}
 
 	public void startListener() throws IOException {
-		WatchService ws = root.getFileSystem().newWatchService();
+		ws = root.getFileSystem().newWatchService();
 		root.register(ws, java.nio.file.StandardWatchEventKinds.ENTRY_MODIFY);
 	}
 

### 2023-11-05 InverseIndex/Indexer/src/main/java/es/ulpgc/bigdata/inverse_index/indexer/Main.java

@@ -15,7 +15,7 @@ public class Main {
 			System.exit(1);
 		}
 		FileDatalake datalake = new FileDatalake(Path.of(args[0]));
-		Datamart datamart = new FileDatamart(Path.of(args[1]));
+		Datamart datamart = new SqlDatamart(Path.of(args[1]));
 		Indexer indexer = new Indexer(datalake, datamart);
 		indexer.index();
 	}

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/Controller.java

@@ -1,11 +1,0 @@
-package es.ulpgc.bigdata.inverse_index;
-
-
-
-
-public class Controller {
-    public void startServers() {
-        SparkWebService sparkWebService = new SparkWebService();
-        sparkWebService.startServer();
-    }
-}

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/Document.java

@@ -1,0 +1,19 @@
+package es.ulpgc.bigdata.inverse_index;
+
+public class Document {
+	int id;
+		public String title;
+		public String author;
+		public String date;
+		public String language;
+		public String content;
+
+		public Document(int id, String title, String author, String date, String language, String content) {
+				this.id = id;
+				this.title = title;
+				this.author = author;
+				this.date = date;
+				this.language = language;
+				this.content = content;
+		}
+}

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/FileDatalake.java

@@ -1,0 +1,31 @@
+package es.ulpgc.bigdata.inverse_index;
+
+import com.google.gson.Gson;
+import com.google.gson.JsonObject;
+
+import java.io.IOException;
+import java.nio.file.Files;
+import java.nio.file.Path;
+
+public class FileDatalake {
+	Path root;
+	private static final Gson gson = new Gson();
+
+	public FileDatalake(Path root) {
+		this.root = root;
+	}
+
+	public Document getDocument(int id) throws IOException {
+		Path documentPath = root.resolve(id + ".json");
+		String documentJson = Files.readString(documentPath);
+		JsonObject documentObj = gson.fromJson(documentJson, JsonObject.class);
+		return new Document(
+			id,
+			documentObj.get("title") == null ? null : documentObj.get("title").getAsString(),
+			documentObj.get("author") == null ? null : documentObj.get("author").getAsString(),
+			documentObj.get("date") == null ? null : documentObj.get("date").getAsString(),
+			documentObj.get("lang") == null ? null : documentObj.get("lang").getAsString(),
+			documentObj.get("text") == null ? null : documentObj.get("text").getAsString()
+		);
+	}
+}

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/Main.java

@@ -1,7 +1,21 @@
 package es.ulpgc.bigdata.inverse_index;
 
+import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
+import es.ulpgc.bigdata.inverse_index.datamart.file.FileDatamart;
+import es.ulpgc.bigdata.inverse_index.datamart.sql.SqlDatamart;
+
+import java.nio.file.Path;
+import java.sql.SQLException;
+
 public class Main {
-	public static void main(String[] args) {
-		new Controller().startServers();
+	public static void main(String[] args) throws SQLException {
+		if (args.length < 2) {
+			System.err.println("The query engine needs a path to the datalake and datamart");
+			System.exit(1);
+		}
+		FileDatalake datalake = new FileDatalake(Path.of(args[0]));
+		Datamart datamart = new SqlDatamart(Path.of(args[1]));
+		SparkWebService webService = new SparkWebService(datalake, datamart);
+		webService.startServer();
 	}
 }

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/SparkWebService.java

@@ -4,39 +4,98 @@ package es.ulpgc.bigdata.inverse_index;
 
 
 import com.google.gson.Gson;
+import com.google.gson.JsonArray;
+import com.google.gson.JsonObject;
+import es.ulpgc.bigdata.inverse_index.datamart.Datamart;
 import spark.Spark;
 
 import java.util.List;
+import java.util.Set;
 
 public class SparkWebService {
+    private final static int SUMMARY_LENGTH = 200;
+    private final static int MAX_LIMIT = 30;
+    private final Datamart datamart;
+    private final FileDatalake datalake;
+    Gson gson = new Gson();
+
+    public SparkWebService(FileDatalake datalake, Datamart datamart) {
+        this.datalake = datalake;
+        this.datamart = datamart;
+    }
 
     public void startServer() {
         Spark.port(4567);
 
         Spark.get("/v1/search", (request, response) -> {
             String word = request.queryParams("word");
-
-            if (word != null) {
-                try {
-                    SqliteReader sqliteReader = new SqliteReader();
-                    List<String> books = sqliteReader.getBooksForWord(word);
-
-                    if (!books.isEmpty()) {
-                        Gson gson = new Gson();
-                        response.type("application/json");
-                        return gson.toJson(books);
-                    } else {
-                        response.status(404); // Not Found
-                        return "Documents not found for the specified word.";
-                    }
-                } catch (Exception e) {
-                    response.status(400); // Bad Request
-                    return "Error processing the request: " + e.getMessage();
+            if (word == null) {
+                response.status(400);
+                return "Missing word parameter\n";
+            }
+            // pagination
+            String offsetStr = request.queryParams("offset");
+            String limitStr = request.queryParams("limit");
+            int offset = offsetStr == null ? 0 : Integer.parseInt(offsetStr);
+            int limit = limitStr == null ? 10 : Integer.parseInt(limitStr);
+            limit = Math.min(limit, MAX_LIMIT);
+            try {
+                Set<Integer> documentIds = datamart.index(word);
+                // get a sorted list of document ids
+                List<Integer> sortedIds = documentIds.stream().sorted().toList();
+                response.type("application/json");
+                JsonArray documents = new JsonArray();
+                for (int i = offset; i < Math.min(offset + limit, sortedIds.size()); i++) {
+                    int id = sortedIds.get(i);
+                    Document document = datalake.getDocument(id);
+                    JsonObject el = summaryJsonObject(id, document);
+                    documents.add(el);
                 }
-            } else {
[…]

### 2023-11-05 InverseIndex/QueryEngine/src/main/java/es/ulpgc/bigdata/inverse_index/SqliteReader.java

@@ -1,31 +1,0 @@
-package es.ulpgc.bigdata.inverse_index;
-
-import java.sql.Connection;
-import java.sql.DriverManager;
-import java.sql.PreparedStatement;
-import java.sql.ResultSet;
-import java.util.ArrayList;
-import java.util.List;
-
-public class SqliteReader {
-
-    public List<String> getBooksForWord(String word) {
-        List<String> books = new ArrayList<>();
-
-        String url = "jdbc:sqlite:datamart.db";
-
-        try (Connection connection = DriverManager.getConnection(url);
-             PreparedStatement preparedStatement = connection.prepareStatement("SELECT book FROM words WHERE word = ?")) {
-            preparedStatement.setString(1, word);
-            ResultSet resultSet = preparedStatement.executeQuery();
-
-            while (resultSet.next()) {
-                String book = resultSet.getString("book");
-                books.add(book);
-            }
-        } catch (Exception e) {
-            e.printStackTrace();
-        }
-        return books;
-    }
-}

### 2023-12-10 latexJava/paper3.tex
Added paper for 3rd turn in

\documentclass{article}

\usepackage{minted}
\usepackage{hyperref}

\title{Crawler and Inverted Index in Java}

\newcommand{\authorblock}[1]{\begin{tabular}{@{}c@{}}#1\end{tabular}}

\author{\centering\begin{tabular}{ccc}
	\authorblock{
		Aurora Zuoris\\
		\normalsize{aurora.zuoris101@alu.ulgpc.es}
	} &
	\authorblock{
	Alejandra Ruiz de Adana Fleitas\\
	\normalsize{alejandra.ruiz104@alu.ulpgc.es}
	} \\ \\
	\authorblock{
	Lam Truong Nguyen\\
	\normalsize{lam.nguyen101@alu.ulpgc.es}
	} &
	\authorblock{
	Aris Vazdekis Soria\\
	\normalsize{aris.vazdekis101@alu.ulpgc.es}
	} \\ \\
	\authorblock{
	Jaime Ballesteros Domínguez\\
	\normalsize{jaime.ballesteros101@alu.ulpgc.es}
	} &
	\authorblock{
	Anna Barbara Król\\
	\normalsize{anna.krol101@alu.ulpgc.es}
	}
\end{tabular}}

\begin{document}
\maketitle
\abstract{ 
In this project, we undertook the task of enhancing search efficiency among a wide variety of text documents. The primary challenge we faced was the need to quickly access documents containing specific terms within an extensive library. Our code encompasses three concurrent modules: Crawler, Indexer and QueryEngine, all working in unison to ensure seamless operation. The project implementation involves a deployment model in a cluster environment, utilising technologies such as Nginx and Docker to ensure scalability and efficient resource utilization.

}

\section{Introduction}
In today's world there is an ever increasing
number of documents that are being created and stored digitally.
Thus the need to easily find and access these documents becomes
ever more important. The 'Query Engine' module enables searching for and retrieving specific books within this extensive digital library. This paper delves into the systematic refinement and development of the Query Engine, Datamart, and containerization modules, explaining the enhancements introduced to bolster the effectiveness and scalability of our information retrieval system.

\section{Methodology}

Our project follows a systematic approach, divided into three major modules: the Crawler,
Inverted Index and Query Engine. Developing and enhancing our project involved refining the Query Engine module,
implementing significant changes in the Datamart module, and integrating containerization for improved deployment.
Our approach included optimizing classes by introducing directory structure configurations, transaction
management and improving overall code organization.Additionally, we utilised Docker and crafted a Dockerfile to encapsulate the QueryEngine, facilitating seamless deployment.

\section{Query Engine}

The Query Engine module is responsible for providing an API interface and search functionality for indexed documents.
This section provides an overview of the key classes and their interactions within the Query Engine module.

\begin{itemize}
\item
The \texttt{SparkWebService} class utilizes the Spark library to launch an HTTP server. This server listens on a specified port and handles HTTP requests, particularly GET requests. It provides a single main query, \texttt{/v1/search}, allowing users to search for documents based on keywords.
\end{itemize}

The \texttt{Main} class contains the \texttt{main} function, which serves as the entry point for the Query Engine module.
It primarily initializes a \texttt{SparkWebService} object and starts the API server.

\section{Datamart Changes}

In this delivery, we have refined Datamart module to introduce enhancements and improvements.
One change in the functionality is that now the datamart will contain the metadata of the documents, including a short summary of the document.
This way the query engine can provide more information about the documents without needing to have access to the datalake.

\begin{itemize}

\item
\texttt{SqlDatamart class} :

This class was improved by adding a debounce mechanism to make commiting to it much more efficient.
The second version introduces a debounceCommit method that schedules a commit after a specified delay, cancelling any previously scheduled commits.
This way, the datamart is only committed once after a set of changes, instead of committing after each change.

\item
\texttt{Metadata class} :

This class is a simple data structure that encapsulates metadata information associated with a document in the inverse index project.
It provides a convenient way to organize and pass around information about a document.
It has a constructor that takes values for each of the six metadata final fields:
\begin{itemize}
    \item 
    id: the document ID
    \item 
    date: a string representing the date of the document
    \item 
    author: a string representing the author of the document
    \item 
    title: a string representing the title of the document
    \item 
    lang: a string representing the language of the document
    \item 
    text: a string representing the text content of the document
\end{itemize}

The use of final fields ensures that the values of these fields cannot be changed once they are set in the constructor, making the Metadata objects immutable.
\end{itemize}

\section{Containerization}
\subsection{Introduction}
Containerization has become a fundamental aspect of modern software development, providing a streamlined approach to packaging, distributing, and running applications across various environments. In our project, containerization is employed to enhance the deployment and execution process of the QueryEngine application. This section delves into the utilization of Docker and the creation of a Dockerfile to encapsulate the QueryEngine in a containerized environment.
\subsection{Dockerfile Explanation}
The approach taken to containerize the QueryEngine was to compile it outside the container into a JAR file, and then use a minimal openjdk image to run the JAR file inside the container.
This approach was chosen because it is simple and efficient, and it allows us to use the same JAR file in both the containerized and non-containerized environments.
The Dockerfile is a description used by docker to build a Docker image.
It sets up an environment for running a QueryEngine in a Docker container.
It defines volumes for the Datamart data, copies the application JAR file into the container, and specifies the default command to run the Java application.
This configuration is designed to facilitate the deployment and execution of the QueryEngine in a Dockerized environment.

\begin{itemize}
\item 
\texttt{FROM openjdk:17} : This line specifies the base image for the Docker image. In our case, it is official OpenJDK 17 image.
\item
\texttt{WORKDIR /app} : Sets the working directory inside the container to /app. This is the directory where subsequent commands will be executed.
\item
\texttt{VOLUME /datalake} :
Creates a Docker volume named /datalake. It is used to persist data outside of the container, and in this case to store Datalake data.
\item
\texttt{VOLUME /datamart} :
Creates another Docker volume named /datamart to store Datamart data.
\item
\texttt{COPY target/QueryEngine.jar} :
Copies the JAR file named QueryEngine.jar from the target directory of the build context into the current working directory (/app) inside the Docker container.
\item
\texttt{CMD ["java", "-jar", "/app/QueryEngine.jar", "/datalake", "/datamart"]}:
Specifies the default command to run when the container starts. In this case, it executes the Java application using the JAR file (QueryEngine.jar) located in the /app directory. It also passes /datalake and /datamart as command-line arguments to the Java application, indicating the paths to their directories.
\end{itemize}

\section{Loadbalancer and Nginx configuration}
\subsection{Loadbalancing}
The inverted index serves as a fundamental component in information retrieval systems, and ensuring its scalability and responsiveness becomes paramount as the volume of data and user queries increases. Within this context, load balancing with Nginx emerges as a critical mechanism to efficiently distribute query requests among multiple instances of the inverted index and query engine services. The development of large-scale inverted index systems is motivated by the need for efficient and rapid information retrieval. However, as these systems evolve, scaling becomes a challenge, necessitating effective load balancing strategies. 
We use Nginx as a versatile load balancer within a distributed inverted index project to optimize resource utilization and enhance system performance.

This too is containerized using docker for ease of deployment on any environment.
\subsection{Nginx configuration for testing purposes}

The provided Nginx configuration represents a basic setup for testing purposes in a distributed system, with a focus on proxying HTTP requests to a Spark server.
\begin{itemize}
    \item \texttt{Events Block:}

    The \texttt{events} block establishes global parameters related to the Nginx worker processes. Specifically, it sets the maximum number of connections per worker process to 1024. This parameterization is critical for controlling resource allocation in a test environment, laying the groundwork for subsequent HTTP request handling.

    \item \texttt{HTTP Block:}

    Within the \texttt{http} block, an \texttt{upstream} directive defines a logical grouping of backend servers under the alias \texttt{spark\_servers}. This block, although configured with a singular backend server at \texttt{192.168.1.57:8080}, is indicative of a preliminary setting for an upstream server group. Such configuration precedes the implementation of load balancing mechanisms in a more comprehensive deployment.

    \item \texttt{Server Block:}

    The \texttt{server} block encapsulates the HTTP server configuration, specifying that it listens on port 80 and is associated with the IP address \texttt{192.168.1.57}. This configuration signifies the entry point for incoming HTTP requests.

    \item \texttt{Location Block for \texttt{/v1/search}:}

    The \texttt{location} block targeting the path \texttt{/v1/search} establishes a \texttt{proxy\_pass} directive, directing requests to the specified backend server group (\texttt{spark\_servers}) at the corresponding path (\texttt{/v1/search}). This configuration delineates the handling of HTTP requests related to search functionality within the proxied environment.

    \item \texttt{Location Block using a Regex:}

    The subsequent \texttt{location} block, utilizing a regular expression \texttt{\^/v1/document/(?<id>\d+)\$}, refines the proxying mechanism for requests matching the specified pattern. Capturing the numeric identifier (\texttt{\$id}) from the matched pattern, this configuration directs requests to the backend server group (\texttt{spark\_servers}) at the path \texttt{/v1/document/} followed by the extracted identifier.

\end{itemize}

In summary, this Nginx configuration outlines a rudimentary setup aimed at testing the proxying of HTTP requests to a Spark server. While adhering to the specificities of a controlled test environment, this configuration lays the foundation for subsequent elaboration on load balancing strategies and scalability measures within the distributed system under examination.

\section{Results and conclusions}

In conclusion, the development undertaken in the Query Engine, Datamart, and containerization modules have yielded significant improvements in the overall functionality, efficiency, and deployment of our information retrieval system. Datamart enhancements contribute to clearer code and potential optimization, while improved Query Engine classes ensure a robust API interface and efficient search functionality. The utilisation of the Docker platform, enhances the deployment process by encapsulating the Query Engine.
The Implementatio on a cluster facilitates distribution and parallelization of tasks, thus improving overall system responsiveness.

The code of this project can be found in the following repository: \url{https://github.com/Aurora2500/inverse-index-big-data}

\section{Future work}

There are various ways in which this project could be improved.
It might start to be interesting to use caching to improve the performance of the query engine.
Aditionally it would be of interest to create a front end for the query engine, so that it can be used by users without needing to use the API directly.

\end{document}
